---
title: "KI Reef Fish Data - Exploratory Plots"
author: "Jennifer Magel"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_depth: 2
---

Summary plots for the 2013, 2015 and 2017 Kiritimati reef fish survey data.

```{r setup, include = FALSE}
## Load data
load("../Data/KI_UVC_13_15_17_trans.Rdata")
load("../Data/KI_UVC_13_15_17.Rdata")
load("../Data/KI_UVC_13_15_17_BM_trans.Rdata")

## Load necessary packages
library(dplyr)
library(ggplot2)
library(RColorBrewer)

## Set theme for plots
theme_set(theme_bw() + theme(plot.title = element_text(hjust = 0.5)) + 
            theme(axis.text.x = element_text(size = 14, color = "black"), 
                 axis.text.y = element_text(size = 14, color = "black"), 
                 axis.ticks = element_blank(),
                 axis.title.y = element_text(size = 17, margin = margin(0,20,0,0)),
                 axis.title.x = element_text(size = 17, margin = margin(20,0,0,0)),
                 plot.title = element_text(size = 20, margin = margin(0,0,15,0)),
                 plot.margin = margin(10,10,10,20), 
                 strip.background = element_rect(fill = "black"),
                 strip.text = element_text(colour = "white", size = 12),
                 panel.border = element_rect(color = "black", fill = NA, size = 1),
                 panel.grid.major = element_blank(), panel.grid.minor = element_blank()))

## Find which sites are present at each time point
sites_13 <- unique(ki_fish$Site[ki_fish$Year == "2013"])
sites_15 <- unique(ki_fish$Site[ki_fish$Year == "2015"])
sites_17 <- unique(ki_fish$Site[ki_fish$Year == "2017"])

# Sites surveyed before/during the El Nino
sites_BD <- intersect(sites_13, sites_15)
# Sites surveyed before/after the El Nino
sites_BA <- intersect(sites_13, sites_17)
# Sites surveyed in all three time points
sites_BDA <- Reduce(intersect, list(sites_13, sites_15, sites_17))
  
## Filter for sites present in all years
ki_fish <- filter(ki_fish, Site %in% sites_BDA)
ki_fish_BM <- filter(ki_fish_BM, Site %in% sites_BDA)

## Order human disturbance levels
levels(ki_fish$f.pressure)
ki_fish$f.pressure <- factor(ki_fish$f.pressure, levels(factor(ki_fish$f.pressure))[c(5,2,3,1,4)])

levels(ki_fish_BM$f.pressure)
ki_fish_BM$f.pressure <- factor(ki_fish_BM$f.pressure, levels(factor(ki_fish_BM$f.pressure))[c(5,2,3,1,4)])

## Order sites for plotting
levels(ki_fish$Site)
ki_fish$Site <- factor(ki_fish$Site, levels(factor(ki_fish$Site))[c(4,5,7,10,1,11,3,6,13,12,2,8,9)])
ki_fish$Site <- factor(ki_fish$Site, levels(factor(ki_fish$Site))[c(8,3,11,1,2,10,9,5,7,12,13,4,6)])

levels(ki_fish_BM$Site)
ki_fish_BM$Site <- factor(ki_fish_BM$Site, levels(factor(ki_fish_BM$Site))[c(4,5,7,10,1,11,3,6,13,12,2,8,9)])
ki_fish_BM$Site <- factor(ki_fish_BM$Site, levels(factor(ki_fish_BM$Site))[c(8,3,11,1,2,10,9,5,7,12,13,4,6)])
```


# Total Abundance
## All Fish

```{r RF_AB, echo = FALSE}
p1 <- ggplot(ki_fish, aes(Site, AB_total)) + geom_bar(aes(fill = Year), stat = "identity", position = "dodge")
p1 <- p1 + xlab("Site") + ylab("Mean Abundance") + labs(title = "Total Fish Abundance")
p1 <- p1 + scale_fill_manual(values = c("#3399CC", "#99CCFF", "#006699"))
p1

p1b <- ggplot(ki_fish, aes(Year, AB_total)) + geom_boxplot(aes(fill = Year))
p1b <- p1b + xlab("Year") + ylab("Mean Abundance") + labs(title = "Total Fish Abundance")
p1b <- p1b + guides(fill = FALSE) + scale_fill_manual(values = c("#3399CC", "#99CCFF", "#006699"))
p1b <- p1b + ylim(0,3000)
p1b

p1c <- ggplot(ki_fish, aes(f.pressure, AB_total)) + geom_boxplot(aes(fill = f.pressure))
p1c <- p1c + xlab("Human Disturbance") + ylab("Mean Abundance") + labs(title = "Total Fish Abundance")
p1c <- p1c +guides(fill = FALSE) + scale_fill_manual(values = c("#01665E", "#80CDC1", "#DFC27D", "#BF812D", "#663300"))
p1c <- p1c + ylim(0,3000)
p1c
```


# Functional Group Abundance
## Corallivores

```{r RF_AB_coral, echo = FALSE}
p3 <- ggplot(ki_fish, aes(Site, AB_coral)) + geom_bar(aes(fill = Year), stat = "identity", position = "dodge")
p3 <- p3 + xlab("Site") + ylab("Mean Abundance") + labs(title = "Corallivore Abundance")
p3 <- p3 + scale_fill_manual(values = c("#3399CC", "#99CCFF", "#006699"))
p3

p3b <- ggplot(ki_fish, aes(Year, AB_coral)) + geom_boxplot(aes(fill = Year))
p3b <- p3b + xlab("Year") + ylab("Mean Abundance") + labs(title = "Corallivore Abundance")
p3b <- p3b + guides(fill = FALSE) + scale_fill_manual(values = c("#3399CC", "#99CCFF", "#006699"))
p3b <- p3b + ylim(0,50)
p3b

p3c <- ggplot(ki_fish, aes(f.pressure, AB_coral)) + geom_boxplot(aes(fill = f.pressure))
p3c <- p3c + xlab("Human Disturbance") + ylab("Mean Abundance") + labs(title = "Corallivore Abundance")
p3c <- p3c + guides(fill = FALSE) + scale_fill_manual(values = c("#01665E", "#80CDC1", "#DFC27D", "#BF812D", "#663300"))
p3c <- p3c + ylim(0,75)
p3c
```

## Detritivores

```{r RF_AB_det, echo = FALSE}
p4 <- ggplot(ki_fish, aes(Site, AB_det)) + geom_bar(aes(fill = Year), stat = "identity", position = "dodge")
p4 <- p4 + xlab("Site") + ylab("Mean Abundance") + labs(title = "Detritivore Abundance")
p4 <- p4 + scale_fill_manual(values = c("#3399CC", "#99CCFF", "#006699"))
p4

p4b <- ggplot(ki_fish, aes(Year, AB_det)) + geom_boxplot(aes(fill = Year))
p4b <- p4b + xlab("Year") + ylab("Mean Abundance") + labs(title = "Detritivore Abundance (All Sites)")
p4b <- p4b + guides(fill = FALSE) + scale_fill_manual(values = c("#3399CC", "#99CCFF", "#006699"))
p4b <- p4b + ylim(0,50)
p4b

p4c <- ggplot(ki_fish, aes(f.pressure, AB_det)) + geom_boxplot(aes(fill = f.pressure))
p4c <- p4c + xlab("Human Disturbance") + ylab("Mean Abundance") + labs(title = "Detritivore Abundance")
p4c <- p4c + guides(fill = FALSE) + scale_fill_manual(values = c("#01665E", "#80CDC1", "#DFC27D", "#BF812D", "#663300"))
p4c <- p4c + ylim(0,50)
p4c
```

## Generalist Carnivores

```{r RF_AB_gen, echo = FALSE}
p6 <- ggplot(ki_fish, aes(Site, AB_gen)) + geom_bar(aes(fill = Year), stat = "identity", position = "dodge")
p6 <- p6 + xlab("Site") + ylab("Mean Abundance") + labs(title = "Generalist Carnivore Abundance")
p6 <- p6 + scale_fill_manual(values = c("#3399CC", "#99CCFF", "#006699"))
p6

p6b <- ggplot(ki_fish, aes(Year, AB_gen)) + geom_boxplot(aes(fill = Year))
p6b <- p6b + xlab("Year") + ylab("Mean Abundance") + labs(title = "Generalist Carnivore Abundance")
p6b <- p6b + guides(fill = FALSE) + scale_fill_manual(values = c("#3399CC", "#99CCFF", "#006699"))
p6b <- p6b + ylim(0,100)
p6b

p6c <- ggplot(ki_fish, aes(f.pressure, AB_gen)) + geom_boxplot(aes(fill = f.pressure))
p6c <- p6c + xlab("Human Disturbance") + ylab("Mean Abundance") + labs(title = "Generalist Carnivore Abundance")
p6c <- p6c + guides(fill = FALSE) + scale_fill_manual(values = c("#01665E", "#80CDC1", "#DFC27D", "#BF812D", "#663300"))
p6c <- p6c + ylim(0,100)
p6c
```

## Herbivores

```{r RF_AB_herb, echo = FALSE}
p7 <- ggplot(ki_fish, aes(Site, AB_herb)) + geom_bar(aes(fill = Year), stat = "identity", position = "dodge")
p7 <- p7 + xlab("Site") + ylab("Mean Abundance") + labs(title = "Herbivore Abundance")
p7 <- p7 + scale_fill_manual(values = c("#3399CC", "#99CCFF", "#006699"))
p7

p7b <- ggplot(ki_fish, aes(Year, AB_herb)) + geom_boxplot(aes(fill = Year))
p7b <- p7b + xlab("Year") + ylab("Mean Abundance") + labs(title = "Herbivore Abundance")
p7b <- p7b + guides(fill = FALSE) + scale_fill_manual(values = c("#3399CC", "#99CCFF", "#006699"))
p7b

p7c <- ggplot(ki_fish, aes(f.pressure, AB_herb)) + geom_boxplot(aes(fill = f.pressure))
p7c <- p7c + xlab("Human Disturbance") + ylab("Mean Abundance") + labs(title = "Herbivore Abundance")
p7c <- p7c + guides(fill = FALSE) + scale_fill_manual(values = c("#01665E", "#80CDC1", "#DFC27D", "#BF812D", "#663300"))
p7c
```

## Invertivores

```{r RF_AB_inv, echo = FALSE}
p8 <- ggplot(ki_fish, aes(Site, AB_inv)) + geom_bar(aes(fill = Year), stat = "identity", position = "dodge")
p8 <- p8 + xlab("Site") + ylab("Mean Abundance") + labs(title = "Invertivore Abundance")
p8 <- p8 + scale_fill_manual(values = c("#3399CC", "#99CCFF", "#006699"))
p8

p8b <- ggplot(ki_fish, aes(Year, AB_inv)) + geom_boxplot(aes(fill = Year))
p8b <- p8b + xlab("Year") + ylab("Mean Abundance") + labs(title = "Invertivore Abundance")
p8b <- p8b + guides(fill = FALSE) + scale_fill_manual(values = c("#3399CC", "#99CCFF", "#006699"))
p8b <- p8b + ylim(0,200)
p8b

p8c <- ggplot(ki_fish, aes(f.pressure, AB_inv)) + geom_boxplot(aes(fill = f.pressure))
p8c <- p8c + xlab("Human Disturbance") + ylab("Mean Abundance") + labs(title = "Invertivore Abundance")
p8c <- p8c + guides(fill = FALSE) + scale_fill_manual(values = c("#01665E", "#80CDC1", "#DFC27D", "#BF812D", "#663300"))
p8c
```

## Omnivores

```{r RF_AB_omn, echo = FALSE}
p9 <- ggplot(ki_fish, aes(Site, AB_omn)) + geom_bar(aes(fill = Year), stat = "identity", position = "dodge")
p9 <- p9 + xlab("Site") + ylab("Mean Abundance") + labs(title = "Omnivore Abundance")
p9 <- p9 + scale_fill_manual(values = c("#3399CC", "#99CCFF", "#006699"))
p9

p9b <- ggplot(ki_fish, aes(Year, AB_omn)) + geom_boxplot(aes(fill = Year))
p9b <- p9b + xlab("Year") + ylab("Mean Abundance") + labs(title = "Omnivore Abundance")
p9b <- p9b + guides(fill = FALSE) + scale_fill_manual(values = c("#3399CC", "#99CCFF", "#006699"))
p9b

p9c <- ggplot(ki_fish, aes(f.pressure, AB_omn)) + geom_boxplot(aes(fill = f.pressure))
p9c <- p9c + xlab("Human Disturbance") + ylab("Mean Abundance") + labs(title = "Omnivore Abundance")
p9c <- p9c + guides(fill = FALSE) + scale_fill_manual(values = c("#01665E", "#80CDC1", "#DFC27D", "#BF812D", "#663300"))
p9c
```

## Piscivores

```{r RF_AB_pisc, echo = FALSE}
p10 <- ggplot(ki_fish, aes(Site, AB_pisc)) + geom_bar(aes(fill = Year), stat = "identity", position = "dodge")
p10 <- p10 + xlab("Site") + ylab("Mean Abundance") + labs(title = "Piscivore Abundance")
p10 <- p10 + scale_fill_manual(values = c("#3399CC", "#99CCFF", "#006699"))
p10

p10b <- ggplot(ki_fish, aes(Year, AB_pisc)) + geom_boxplot(aes(fill = Year))
p10b <- p10b + xlab("Year") + ylab("Mean Abundance") + labs(title = "Piscivore Abundance")
p10b <- p10b + guides(fill = FALSE) + scale_fill_manual(values = c("#3399CC", "#99CCFF", "#006699"))
p10b <- p10b + ylim(0,50)
p10b

p10c <- ggplot(ki_fish, aes(f.pressure, AB_pisc)) + geom_boxplot(aes(fill = f.pressure))
p10c <- p10c + xlab("Human Disturbance") + ylab("Mean Abundance") + labs(title = "Piscivore Abundance")
p10c <- p10c + guides(fill = FALSE) + scale_fill_manual(values = c("#01665E", "#80CDC1", "#DFC27D", "#BF812D", "#663300"))
p10c <- p10c + ylim(0,75)
p10c
```

## Planktivores

```{r RF_AB_plank, echo = FALSE}
p11 <- ggplot(ki_fish, aes(Site, AB_plank)) + geom_bar(aes(fill = Year), stat = "identity", position = "dodge")
p11 <- p11 + xlab("Site") + ylab("Mean Abundance") + labs(title = "Planktivore Abundance")
p11 <- p11 + scale_fill_manual(values = c("#3399CC", "#99CCFF", "#006699"))
p11

p11b <- ggplot(ki_fish, aes(Year, AB_plank)) + geom_boxplot(aes(fill = Year))
p11b <- p11b + xlab("Year") + ylab("Mean Abundance") + labs(title = "Planktivore Abundance")
p11b <- p11b + guides(fill = FALSE) + scale_fill_manual(values = c("#3399CC", "#99CCFF", "#006699"))
p11b <- p11b + ylim(0,3000)
p11b

p11c <- ggplot(ki_fish, aes(f.pressure, AB_plank)) + geom_boxplot(aes(fill = f.pressure))
p11c <- p11c + xlab("Human Disturbance") + ylab("Mean Abundance") + labs(title = "Planktivore Abundance")
p11c <- p11c + guides(fill = FALSE) + scale_fill_manual(values = c("#01665E", "#80CDC1", "#DFC27D", "#BF812D", "#663300"))
p11c <- p11c + ylim(0,3000)
p11c
```


# Biomass
## All Fish

```{r RF_BM, echo = FALSE}
p1c <- ggplot(ki_fish_BM, aes(Site, BM_total)) + geom_bar(aes(fill = Year), stat = "identity", position = "dodge")
p1c <- p1c + xlab("Site") + ylab("Mean Biomass (kg)") + labs(title = "Total Fish Biomass")
p1c <- p1c + scale_fill_manual(values = c("#3399CC", "#99CCFF", "#006699"))
p1c

p1d <- ggplot(ki_fish_BM, aes(Year, BM_total)) + geom_boxplot(aes(fill = Year))
p1d <- p1d + xlab("Year") + ylab("Mean Biomass (kg)") + labs(title = "Total Fish Biomass")
p1d <- p1d + guides(fill = FALSE) + scale_fill_manual(values = c("#3399CC", "#99CCFF", "#006699"))
p1d <- p1d + ylim(0,50)
p1d

p1e <- ggplot(ki_fish_BM, aes(f.pressure, BM_total)) + geom_boxplot(aes(fill = f.pressure))
p1e <- p1e + xlab("Human Disturbance") + ylab("Mean Biomass (kg)") + labs(title = "Total Fish Biomass")
p1e <- p1e +guides(fill = FALSE) + scale_fill_manual(values = c("#01665E", "#80CDC1", "#DFC27D", "#BF812D", "#663300"))
p1e <- p1e + ylim(0,75)
p1e
```

## Corallivores

```{r RF_BM_coral, echo = FALSE}
p3d <- ggplot(ki_fish_BM, aes(Site, BM_coral)) + geom_bar(aes(fill = Year), stat = "identity", position = "dodge")
p3d <- p3d + xlab("Site") + ylab("Mean Biomass (kg)") + labs(title = "Corallivore Biomass")
p3d <- p3d + scale_fill_manual(values = c("#3399CC", "#99CCFF", "#006699"))
p3d

p3e <- ggplot(ki_fish_BM, aes(Year, BM_coral)) + geom_boxplot(aes(fill = Year))
p3e <- p3e + xlab("Year") + ylab("Mean Biomass (kg)") + labs(title = "Corallivore Biomass")
p3e <- p3e + guides(fill = FALSE) + scale_fill_manual(values = c("#3399CC", "#99CCFF", "#006699"))
p3e <- p3e + ylim(0,1)
p3e

p3f <- ggplot(ki_fish_BM, aes(f.pressure, BM_coral)) + geom_boxplot(aes(fill = f.pressure))
p3f <- p3f + xlab("Human Disturbance") + ylab("Mean Biomass (kg)") + labs(title = "Corallivore Biomass")
p3f <- p3f + guides(fill = FALSE) + scale_fill_manual(values = c("#01665E", "#80CDC1", "#DFC27D", "#BF812D", "#663300"))
p3f <- p3f + ylim(0,1)
p3f
```

## Detritivores

```{r RF_BM_det, echo = FALSE}
p4d <- ggplot(ki_fish_BM, aes(Site, BM_det)) + geom_bar(aes(fill = Year), stat = "identity", position = "dodge")
p4d <- p4d + xlab("Site") + ylab("Mean Biomass (kg)") + labs(title = "Detritivore Biomass")
p4d <- p4d + scale_fill_manual(values = c("#3399CC", "#99CCFF", "#006699"))
p4d

p4e <- ggplot(ki_fish_BM, aes(Year, BM_det)) + geom_boxplot(aes(fill = Year))
p4e <- p4e + xlab("Year") + ylab("Mean Biomass (kg)") + labs(title = "Detritivore Biomass")
p4e <- p4e + guides(fill = FALSE) + scale_fill_manual(values = c("#3399CC", "#99CCFF", "#006699"))
p4e

p4f <- ggplot(ki_fish_BM, aes(f.pressure, BM_det)) + geom_boxplot(aes(fill = f.pressure))
p4f <- p4f + xlab("Human Disturbance") + ylab("Mean Biomass (kg)") + labs(title = "Detritivore Biomass")
p4f <- p4f + guides(fill = FALSE) + scale_fill_manual(values = c("#01665E", "#80CDC1", "#DFC27D", "#BF812D", "#663300"))
p4f
```

## Generalist Carnivores

```{r RF_BM_gen, echo = FALSE}
p6d <- ggplot(ki_fish_BM, aes(Site, BM_gen)) + geom_bar(aes(fill = Year), stat = "identity", position = "dodge")
p6d <- p6d + xlab("Site") + ylab("Mean Biomass (kg)") + labs(title = "Generalist Carnivore Biomass")
p6d <- p6d + scale_fill_manual(values = c("#3399CC", "#99CCFF", "#006699"))
p6d

p6e <- ggplot(ki_fish_BM, aes(Year, BM_gen)) + geom_boxplot(aes(fill = Year))
p6e <- p6e + xlab("Year") + ylab("Mean Biomass (kg)") + labs(title = "Generalist Carnivore Biomass")
p6e <- p6e + guides(fill = FALSE) + scale_fill_manual(values = c("#3399CC", "#99CCFF", "#006699"))
p6e <- p6e + ylim(0,3)
p6e

p6f <- ggplot(ki_fish_BM, aes(f.pressure, BM_gen)) + geom_boxplot(aes(fill = f.pressure))
p6f <- p6f + xlab("Human Disturbance") + ylab("Mean Biomass (kg)") + labs(title = "Generalist Carnivore Biomass")
p6f <- p6f + guides(fill = FALSE) + scale_fill_manual(values = c("#01665E", "#80CDC1", "#DFC27D", "#BF812D", "#663300"))
p6f <- p6f + ylim(0,3)
p6f
```

## Herbivores

```{r RF_BM_herb, echo = FALSE}
p7d <- ggplot(ki_fish_BM, aes(Site, BM_herb)) + geom_bar(aes(fill = Year), stat = "identity", position = "dodge")
p7d <- p7d + xlab("Site") + ylab("Mean Biomass (kg)") + labs(title = "Herbivore Biomass")
p7d <- p7d + scale_fill_manual(values = c("#3399CC", "#99CCFF", "#006699"))
p7d

p7e <- ggplot(ki_fish_BM, aes(Year, BM_herb)) + geom_boxplot(aes(fill = Year))
p7e <- p7e + xlab("Year") + ylab("Mean Biomass (kg)") + labs(title = "Herbivore Biomass")
p7e <- p7e + guides(fill = FALSE) + scale_fill_manual(values = c("#3399CC", "#99CCFF", "#006699"))
p7e <- p7e + ylim(0,25)
p7e

p7f <- ggplot(ki_fish_BM, aes(f.pressure, BM_herb)) + geom_boxplot(aes(fill = f.pressure))
p7f <- p7f + xlab("Human Disturbance") + ylab("Mean Biomass (kg)") + labs(title = "Herbivore Biomass")
p7f <- p7f + guides(fill = FALSE) + scale_fill_manual(values = c("#01665E", "#80CDC1", "#DFC27D", "#BF812D", "#663300"))
p7f
```

## Invertivores

```{r RF_BM_inv, echo = FALSE}
p8d <- ggplot(ki_fish_BM, aes(Site, BM_inv)) + geom_bar(aes(fill = Year), stat = "identity", position = "dodge")
p8d <- p8d + xlab("Site") + ylab("Mean Biomass (kg)") + labs(title = "Invertivore Biomass")
p8d <- p8d + scale_fill_manual(values = c("#3399CC", "#99CCFF", "#006699"))
p8d

p8e <- ggplot(ki_fish_BM, aes(Year, BM_inv)) + geom_boxplot(aes(fill = Year))
p8e <- p8e + xlab("Year") + ylab("Mean Biomass (kg)") + labs(title = "Invertivore Biomass")
p8e <- p8e + guides(fill = FALSE) + scale_fill_manual(values = c("#3399CC", "#99CCFF", "#006699"))
p8e <- p8e + ylim(0,7.5)
p8e

p8f <- ggplot(ki_fish_BM, aes(f.pressure, BM_inv)) + geom_boxplot(aes(fill = f.pressure))
p8f <- p8f + xlab("Human Disturbance") + ylab("Mean Biomass (kg)") + labs(title = "Invertivore Biomass")
p8f <- p8f + guides(fill = FALSE) + scale_fill_manual(values = c("#01665E", "#80CDC1", "#DFC27D", "#BF812D", "#663300"))
p8f <- p8f + ylim(0,5)
p8f
```

## Omnivores

```{r RF_BM_omn, echo = FALSE}
p9d <- ggplot(ki_fish_BM, aes(Site, BM_omn)) + geom_bar(aes(fill = Year), stat = "identity", position = "dodge")
p9d <- p9d + xlab("Site") + ylab("Mean Biomass (kg)") + labs(title = "Omnivore Biomass")
p9d <- p9d + scale_fill_manual(values = c("#3399CC", "#99CCFF", "#006699"))
p9d

p9e <- ggplot(ki_fish_BM, aes(Year, BM_omn)) + geom_boxplot(aes(fill = Year))
p9e <- p9e + xlab("Year") + ylab("Mean Biomass (kg)") + labs(title = "Omnivore Biomass")
p9e <- p9e + guides(fill = FALSE) + scale_fill_manual(values = c("#3399CC", "#99CCFF", "#006699"))
p9e <- p9e + ylim(0,5)
p9e

p9f <- ggplot(ki_fish_BM, aes(f.pressure, BM_omn)) + geom_boxplot(aes(fill = f.pressure))
p9f <- p9f + xlab("Human Disturbance") + ylab("Mean Biomass (kg)") + labs(title = "Omnivore Biomass")
p9f <- p9f + guides(fill = FALSE) + scale_fill_manual(values = c("#01665E", "#80CDC1", "#DFC27D", "#BF812D", "#663300"))
p9f <- p9f + ylim(0,5)
p9f
```

## Piscivores

```{r RF_BM_pisc, echo = FALSE}
p10d <- ggplot(ki_fish_BM, aes(Site, BM_pisc)) + geom_bar(aes(fill = Year), stat = "identity", position = "dodge")
p10d <- p10d + xlab("Site") + ylab("Mean Biomass (kg)") + labs(title = "Piscivore Biomass")
p10d <- p10d + scale_fill_manual(values = c("#3399CC", "#99CCFF", "#006699"))
p10d

p10e <- ggplot(ki_fish_BM, aes(Year, BM_pisc)) + geom_boxplot(aes(fill = Year))
p10e <- p10e + xlab("Year") + ylab("Mean Biomass (kg)") + labs(title = "Piscivore Biomass")
p10e <- p10e + guides(fill = FALSE) + scale_fill_manual(values = c("#3399CC", "#99CCFF", "#006699"))
p10e <- p10e + ylim(0,6)
p10e

p10f <- ggplot(ki_fish_BM, aes(f.pressure, BM_pisc)) + geom_boxplot(aes(fill = f.pressure))
p10f <- p10f + xlab("Human Disturbance") + ylab("Mean Biomass (kg)") + labs(title = "Piscivore Biomass")
p10f <- p10f + guides(fill = FALSE) + scale_fill_manual(values = c("#01665E", "#80CDC1", "#DFC27D", "#BF812D", "#663300"))
p10f <- p10f + ylim(0,5)
p10f
```

## Planktivores

```{r RF_BM_plank, echo = FALSE}
p11d <- ggplot(ki_fish_BM, aes(Site, BM_plank)) + geom_bar(aes(fill = Year), stat = "identity", position = "dodge")
p11d <- p11d + xlab("Site") + ylab("Mean Biomass (kg)") + labs(title = "Planktivore Biomass")
p11d <- p11d + scale_fill_manual(values = c("#3399CC", "#99CCFF", "#006699"))
p11d

p11e <- ggplot(ki_fish_BM, aes(Year, BM_plank)) + geom_boxplot(aes(fill = Year))
p11e <- p11e + xlab("Year") + ylab("Mean Biomass (kg)") + labs(title = "Planktivore Biomass")
p11e <- p11e + guides(fill = FALSE) + scale_fill_manual(values = c("#3399CC", "#99CCFF", "#006699"))
p11e <- p11e + ylim(0,7.5)
p11e

p11f <- ggplot(ki_fish_BM, aes(f.pressure, BM_plank)) + geom_boxplot(aes(fill = f.pressure))
p11f <- p11f + xlab("Human Disturbance") + ylab("Mean Biomass (kg)") + labs(title = "Planktivore Biomass")
p11f <- p11f + guides(fill = FALSE) + scale_fill_manual(values = c("#01665E", "#80CDC1", "#DFC27D", "#BF812D", "#663300"))
p11f <- p11f + ylim(0,7.5)
p11f
```



```{r RF_FC, include = FALSE}
## Calculate average abundance of each functional group (per site)
# Sum abundances per diver 
ki_AB_FG <- ki_full %>% group_by(Year, KI.Date, Site, Transect, Observer, f.pressure, CoarseFG) %>% summarise(abundance = sum(Number))
# Average abundances across divers, within Rep
ki_AB_FG <- ki_AB_FG %>% group_by(Year, KI.Date, Site, Transect, f.pressure, CoarseFG) %>% summarise(mean_abundance = mean(abundance))
# Average abundance across Reps, for each unique site (still separated by date)
ki_AB_FG <- ki_AB_FG %>% group_by(Year, KI.Date, Site, f.pressure, CoarseFG) %>% summarise(mean_abundance = mean(mean_abundance))
# Average abundance for each site, including sites surveyed on multiple days
ki_AB_FG <- ki_AB_FG %>% group_by(Year, Site, f.pressure, CoarseFG) %>% summarise(mean_abundance = mean(mean_abundance))

ki_AB_FG$CoarseFG[ki_AB_FG$CoarseFG == "Corallivore"] <- "Coral."
ki_AB_FG$CoarseFG[ki_AB_FG$CoarseFG == "Detritivore"] <- "Det."
ki_AB_FG$CoarseFG[ki_AB_FG$CoarseFG == "Generalist Carnivore"] <- "Gen."
ki_AB_FG$CoarseFG[ki_AB_FG$CoarseFG == "Herbivore"] <- "Herb."
ki_AB_FG$CoarseFG[ki_AB_FG$CoarseFG == "Invertivore"] <- "Inv."
ki_AB_FG$CoarseFG[ki_AB_FG$CoarseFG == "Omnivore"] <- "Omn."
ki_AB_FG$CoarseFG[ki_AB_FG$CoarseFG == "Piscivore"] <- "Pisc."
ki_AB_FG$CoarseFG[ki_AB_FG$CoarseFG == "Planktivore"] <- "Plank."

my.palette <- brewer.pal(8, "GnBu")

## Create plot
p15 <- ggplot(ki_AB_FG, aes(CoarseFG, log(mean_abundance))) + geom_boxplot(aes(fill = Year))
p15 <- p15 + xlab("Functional Group") + ylab("log Mean Abundance") + labs(title = "Functional Composition (All Sites)")
p15 <- p15 + scale_fill_manual(values = c("#3399CC", "#99CCFF", "#006699"))
p15

p15b <- ggplot(ki_AB_FG, aes(Year, mean_abundance)) + geom_bar(aes(fill = CoarseFG), stat = "identity", position = "dodge")
p15b <- p15b + xlab("Year") + ylab("Mean Abundance") + labs(title = "Functional Composition by Year")
p15b <- p15b + scale_fill_brewer(palette = "PuBu")
p15b
```