---
title: "Acoustic_2019_Explore"
author: "Sean Dimoff"
date: "October 9, 2019"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
---

```{r setup, include=FALSE}
library(ggplot2)
library(cowplot)
library(rmarkdown)
library(knitr)
library(RColorBrewer)
library(GGally)
library(mctest)
library(usdm)

##loading in the ACI/SPL data - wide form

#hourdata
load("../Raw_Data/ACI_BB17hr.Rdata")
load("../Raw_Data/ACI_BB18hr.Rdata")
load("../Raw_Data/ACI_HF17hr.Rdata")
load("../Raw_Data/ACI_HF18hr.Rdata")
load("../Raw_Data/ACI_MF17hr.Rdata")
load("../Raw_Data/ACI_MF18hr.Rdata")

load("../Raw_Data/SPL_BB17hr.Rdata")
load("../Raw_Data/SPL_BB18hr.Rdata")
load("../Raw_Data/SPL_HF17hr.Rdata")
load("../Raw_Data/SPL_HF18hr.Rdata")
load("../Raw_Data/SPL_MF17hr.Rdata")
load("../Raw_Data/SPL_MF18hr.Rdata")

#All time data
load("../Raw_Data/SPL_BB17.Rdata")
load("../Raw_Data/SPL_BB18.Rdata")

#daydata
load("../Raw_Data/ACI_BB17day.Rdata")
load("../Raw_Data/ACI_BB18day.Rdata")
load("../Raw_Data/ACI_HF17day.Rdata")
load("../Raw_Data/ACI_HF18day.Rdata")
load("../Raw_Data/ACI_MF17day.Rdata")
load("../Raw_Data/ACI_MF18day.Rdata")

load("../Raw_Data/SPL_BB17day.Rdata")
load("../Raw_Data/SPL_BB18day.Rdata")
load("../Raw_Data/SPL_HF17day.Rdata")
load("../Raw_Data/SPL_HF18day.Rdata")
load("../Raw_Data/SPL_MF17day.Rdata")
load("../Raw_Data/SPL_MF18day.Rdata")

#loading ACI/SPL long data for boxplots
#ACI
load("../Raw_Data/ACI_BB17hrlong.Rdata")
load("../Raw_Data/ACI_HF17hrlong.Rdata")
load("../Raw_Data/ACI_MF17hrlong.Rdata")
load("../Raw_Data/ACI_BB18hrlong.Rdata")
load("../Raw_Data/ACI_HF18hrlong.Rdata")
load("../Raw_Data/ACI_MF18hrlong.Rdata")

load("../Raw_Data/ACI_MFhrlong.Rdata")
load("../Raw_Data/ACI_HFhrlong.Rdata")
load("../Raw_Data/ACI_BBhrlong.Rdata")

load("../Raw_Data/ACI_BBhr_av.Rdata")
load("../Raw_Data/ACI_HFhr_av.Rdata")
load("../Raw_Data/ACI_MFhr_av.Rdata")

##making year a character
ACI_BB.hr.long$Year <- as.character(ACI_BB.hr.long$Year)
ACI_HF.hr.long$Year <- as.character(ACI_HF.hr.long$Year)
ACI_MF.hr.long$Year <- as.character(ACI_MF.hr.long$Year)

#SPL
load("../Raw_Data/SPL_BB17hrlong.Rdata")
load("../Raw_Data/SPL_HF17hrlong.Rdata")
load("../Raw_Data/SPL_MF17hrlong.Rdata")
load("../Raw_Data/SPL_BB18hrlong.Rdata")
load("../Raw_Data/SPL_HF18hrlong.Rdata")
load("../Raw_Data/SPL_MF18hrlong.Rdata")

load("../Raw_Data/SPL_MFhrlong.Rdata")
load("../Raw_Data/SPL_HFhrlong.Rdata")
load("../Raw_Data/SPL_BBhrlong.Rdata")

load("../Raw_Data/SPL_BBhr_av.Rdata")
load("../Raw_Data/SPL_HFhr_av.Rdata")
load("../Raw_Data/SPL_MFhr_av.Rdata")

#making year a character
SPL_BB.hr.long$Year <- as.character(SPL_BB.hr.long$Year)
SPL_HF.hr.long$Year <- as.character(SPL_HF.hr.long$Year)
SPL_MF.hr.long$Year <- as.character(SPL_MF.hr.long$Year)

##loading in fish call count data
load("../Raw_Data/FC.05hr.Rdata")
load("../Raw_Data/FC.08hr.Rdata")
load("../Raw_Data/FC.32hr.Rdata")
load("../Raw_Data/FC.35hr.Rdata")
load("../Raw_Data/FC.40hr.Rdata")

load("../Raw_Data/FC.CallperDayALL.Rdata")
load("../Raw_Data/FC.CallperDay17.Rdata")
load("../Raw_Data/FC.CallperDay18.Rdata")

load("../Raw_Data/FC.CallperHourALL.Rdata")
load("../Raw_Data/FC.CallperHour17.Rdata")
load("../Raw_Data/FC.CallperHour18.Rdata")

#loading in total dataframe
load("../Raw_Data/AC.DF.Rdata")




##loading in Boat visitation data
load("../Raw_Data/BV.all.Rdata")
load("../Raw_Data/BV.sum.Rdata")





##loading in lunar phase data
load("../Raw_Data/LunarPhase2017.Rdata")
load("../Raw_Data/LunarPhase2018.Rdata")


##loading in fish data
load("../Raw_Data/ki_fishabundance.Rdata")
load("../Raw_Data/ki_fishabundance17.Rdata")
load("../Raw_Data/ki_fishabundance18.Rdata")

load("../Raw_Data/ki_fishaverage.Rdata")
load("../Raw_Data/ki_fishaverage17.Rdata")
load("../Raw_Data/ki_fishaverage18.Rdata")


##loading in the full dataframe with all data
load("../Raw_Data/AC.DF.Rdata")
load("../Raw_Data/AC.DF1.Rdata")

#creating small legend function
#addSmallLegend <- function(myPlot, pointSize = 0.7, textSize = 5, spaceLegend = 0.2) {
#    myPlot +
#        guides(shape = guide_legend(override.aes = list(size = pointSize)),
#               color = guide_legend(override.aes = list(size = pointSize))) +
#        theme(legend.title = element_text(size = textSize), 
#              legend.text  = element_text(size = textSize),
#              legend.key.size = unit(spaceLegend, "lines"))
#}


```
**Exploratory Plots for 2017-2018 Acoustic/Fish Data**

**Purpose** To explore the Acoustic data gathered in 2017 and 2018 to expose important trends between sites, diurnal patterns, fish abundance, lunar phase, and coral reef acoustics.

#Acoustics
**Acoustics Breakdown** All acoustic metrics (SPL and ACI) are broken down into 3 frequency bands: Broadband (All frequencies), High Frequency (Frequencies between 1 kHz - 22 kHz), and Mid Frequency (Frequencies between 160 Hz and 1 kHz)

*Note* 2017 had a 10 minute duty cycle with 5 minutes recording while 2018 had a 15 minute duty cycle with 5 minutes recording, so the number of files averages differs between years

##SPL (Hourly Averages)

### Broadband
Broadband SPL averaged by hour across all days
```{r spl broadband, echo=FALSE}

p.splbb17<- ggplot(data =SPL_BB17.hr.long, aes(x=as.numeric(Hour), y=Broadband_SPL)) + geom_line(aes(color=as.character(Site))) + xlab("Hour") + ylab ("BB_SPL") + theme(legend.position = "bottom", legend.title = element_blank(), axis.title.x = element_blank(), axis.text.x = element_blank()) + scale_color_brewer(palette = "Set1")

#making legend smaller
#p.splbb17 <- addSmallLegend(p.splbb17)

p.splbb18<- ggplot(data =SPL_BB18.hr.long, aes(x=as.numeric(Hour), y=Broadband_SPL)) + geom_line(aes(color=as.character(Site))) + xlab("Hour") + ylab ("BB_SPL") + scale_color_brewer(palette = "Set1") +
  theme(legend.position = "none")

#Horizontal graph
#splbb.h <- plot_grid(p.splbb17, p.splbb18, labels = c("2017", "2018"), align = "h")
#splbb.h

p.splbb <- ggplot(data =SPL_BB.hr.av, aes(x=as.numeric(Hour), y=Broadband_SPL)) + geom_line(aes(color=as.character(Site))) + xlab("Hour") + ylab ("BB_SPL") + scale_color_brewer(palette = "Set1") + ggtitle("Averaged BB SPL") +
  theme(legend.position = "none")

splbb.v <- plot_grid(p.splbb17, p.splbb18, labels = c("2017", "2018"), nrow = 2, align = "v", label_x = .5)

splbb.v
p.splbb

#Combining both into one graph
#p.splbb.both <- ggplot(data =SPL_BB17.hr.long, aes(x=as.numeric(Hour), y=Broadband_SPL)) + geom_line(aes(color=as.character(Site))) + xlab("Hour") + ylab ("BB_SPL") + geom_line(data = SPL_BB.hr.long, aes())


```

### Broadband by site
```{r spl bb by site, echo=FALSE}

#Dataframe needs to be shifted to wide format

#p1 <- ggplot(data =SPL_BB17, aes(x=as.numeric(Hour), y=Broadband_SPL)) + geom_line(aes(color=as.character(Site))) + xlab("Hour") + ylab ("BB_SPL") + theme(legend.position = "bottom", legend.title = element_blank(), axis.title.x = element_blank(), axis.text.x = element_blank()) + scale_color_brewer(palette = "Set1")



```


### High Frequency
High Frequency SPL averaged by hour across all days
```{r spl hf, echo=FALSE}

p.splhf17<- ggplot(data =SPL_HF17.hr.long, aes(x=as.numeric(Hour), y=HF_SPL)) + geom_line(aes(color=as.character(Site))) + xlab("Hour") + ylab ("HF_SPL") + theme(legend.position = "bottom", legend.title = element_blank(), axis.title.x = element_blank(), axis.text.x = element_blank()) + scale_color_brewer(palette = "Set1")

#making legend smaller
#p.splbb17 <- addSmallLegend(p.splbb17)

p.splhf18<- ggplot(data =SPL_HF18.hr.long, aes(x=as.numeric(Hour), y=HF_SPL)) + geom_line(aes(color=as.character(Site))) + xlab("Hour") + ylab ("HF_SPL") + scale_color_brewer(palette = "Set1") +
  theme(legend.position = "none")

p.splhf <- ggplot(data =SPL_HF.hr.av, aes(x=as.numeric(Hour), y=HF_SPL)) + geom_line(aes(color=as.character(Site))) + xlab("Hour") + ylab ("HF_SPL") + scale_color_brewer(palette = "Set1") + ggtitle("Averaged HF SPL")


#Horizontal graph
#splbb.h <- plot_grid(p.splbb17, p.splbb18, labels = c("2017", "2018"), align = "h")
#splbb.h

splhf.v <- plot_grid(p.splhf17, p.splhf18, labels = c("2017", "2018"), nrow = 2, align = "v", label_x = .5)

splhf.v
p.splhf
```

### Mid Frequency
Mid Frequency SPL averaged by hour across all days
```{r spl mf, echo=FALSE}

p.splmf17<- ggplot(data =SPL_MF17.hr.long, aes(x=as.numeric(Hour), y=MF_SPL)) + geom_line(aes(color=as.character(Site))) + xlab("Hour") + ylab ("MF_SPL") + theme(legend.position = "bottom", legend.title = element_blank(), axis.title.x = element_blank(), axis.text.x = element_blank()) + scale_color_brewer(palette = "Set1")

#making legend smaller
#p.splbb17 <- addSmallLegend(p.splbb17)

p.splmf18<- ggplot(data =SPL_MF18.hr.long, aes(x=as.numeric(Hour), y=MF_SPL)) + geom_line(aes(color=as.character(Site))) + xlab("Hour") + ylab ("MF_SPL") + scale_color_brewer(palette = "Set1") +
  theme(legend.position = "none")

p.splmf <- ggplot(data =SPL_MF.hr.av, aes(x=as.numeric(Hour), y=MF_SPL)) + geom_line(aes(color=as.character(Site))) + xlab("Hour") + ylab ("MF_SPL") + scale_color_brewer(palette = "Set1") + ggtitle("Averaged MF SPL")

#Horizontal graph
#splbb.h <- plot_grid(p.splbb17, p.splbb18, labels = c("2017", "2018"), align = "h")
#splbb.h

splmf.v <- plot_grid(p.splmf17, p.splmf18, labels = c("2017", "2018"), nrow = 2, align = "v", label_x = .5)

splmf.v
p.splmf
```


### Boxplots
Distribution of SPL at all frequencies and sites - averaged by hour
```{r spl bp, echo=FALSE}
#Boxplot

p.splbb.bp <- ggplot(data = SPL_BB.hr.long, aes(y = Broadband_SPL, x = Site, fill = Year)) + geom_boxplot() + ylab("SPL")
p.splhf.bp <- ggplot(data = SPL_HF.hr.long, aes(y = HF_SPL, x = Site, fill = Year)) + geom_boxplot() + ylab("SPL")
p.splmf.bp <- ggplot(data = SPL_MF.hr.long, aes(y = MF_SPL, x = Site, fill = Year)) + geom_boxplot() + ylab("SPL")

p.spl.bp <- plot_grid(p.splbb.bp, p.splhf.bp, p.splmf.bp, labels = c("Broadband", "High Frequency", "Mid Frequency"), nrow = 3, align = "v", label_x = .4)

p.spl.bp
```


##ACI (Hourly Averages)


### Broadband
Broadband ACI averaged by hour across all days
```{r aci broadband, echo=FALSE}

p.acibb17<- ggplot(data =ACI_BB17.hr.long, aes(x=as.numeric(Hour), y=Broadband_ACI)) + geom_line(aes(color=as.character(Site))) + xlab("Hour") + ylab ("BB_ACI") + theme(legend.position = "bottom", legend.title = element_blank(), axis.title.x = element_blank(), axis.text.x = element_blank()) + scale_color_brewer(palette = "Set1")

#making legend smaller
#p.acibb17 <- addSmallLegend(p.acibb17)

p.acibb18<- ggplot(data =ACI_BB18.hr.long, aes(x=as.numeric(Hour), y=Broadband_ACI)) + geom_line(aes(color=as.character(Site))) + xlab("Hour") + ylab ("BB_ACI") + scale_color_brewer(palette = "Set1") +
  theme(legend.position = "none")


p.acibb <- ggplot(data =ACI_BB.hr.av, aes(x=as.numeric(Hour), y=Broadband_ACI)) + geom_line(aes(color=as.character(Site))) + xlab("Hour") + ylab ("BB_ACI") + scale_color_brewer(palette = "Set1") + ggtitle("Averaged BB ACI")

#Horizontal graph
#splbb.h <- plot_grid(p.splbb17, p.splbb18, labels = c("2017", "2018"), align = "h")
#splbb.h

acibb.v <- plot_grid(p.acibb17, p.acibb18, labels = c("2017", "2018"), label_x = .5, nrow = 2 )

acibb.v
p.acibb
```

### High Frequency
High Frequency ACI averaged by hour across all days
```{r aci hf, echo=FALSE}

p.acihf17<- ggplot(data =ACI_HF17.hr.long, aes(x=as.numeric(Hour), y=HF_ACI)) + geom_line(aes(color=as.character(Site))) + xlab("Hour") + ylab ("HF_ACI") + theme(legend.position = "bottom", legend.title = element_blank(), axis.title.x = element_blank(), axis.text.x = element_blank()) + scale_color_brewer(palette = "Set1")

#making legend smaller
#p.splbb17 <- addSmallLegend(p.splbb17)

p.acihf18<- ggplot(data =ACI_HF18.hr.long, aes(x=as.numeric(Hour), y=HF_ACI)) + geom_line(aes(color=as.character(Site))) + xlab("Hour") + ylab ("HF_ACI") + scale_color_brewer(palette = "Set1") +
  theme(legend.position = "none")

p.acihf <- ggplot(data =ACI_HF.hr.av, aes(x=as.numeric(Hour), y=HF_ACI)) + geom_line(aes(color=as.character(Site))) + xlab("Hour") + ylab ("HF_ACI") + scale_color_brewer(palette = "Set1") + ggtitle("Averaged HF ACI")
#Horizontal graph
#splbb.h <- plot_grid(p.splbb17, p.splbb18, labels = c("2017", "2018"), align = "h")
#splbb.h

acihf.v <- plot_grid(p.acihf17, p.acihf18, labels = c("2017", "2018"), label_x = .5, nrow = 2 )

acihf.v
p.acihf
```

### Mid Frequency
Mid Frequency ACI averaged by hour across all days
```{r aci mf, echo=FALSE}

p.acimf17<- ggplot(data =ACI_MF17.hr.long, aes(x=as.numeric(Hour), y=MF_ACI)) + geom_line(aes(color=as.character(Site))) + xlab("Hour") + ylab ("MF_ACI") + theme(legend.position = "bottom", legend.title = element_blank(), axis.title.x = element_blank(), axis.text.x = element_blank()) + scale_color_brewer(palette = "Set1")

#making legend smaller
#p.splbb17 <- addSmallLegend(p.splbb17)

p.acimf18<- ggplot(data =ACI_MF18.hr.long, aes(x=as.numeric(Hour), y=MF_ACI)) + geom_line(aes(color=as.character(Site))) + xlab("Hour") + ylab ("MF_ACI") + scale_color_brewer(palette = "Set1") +
  theme(legend.position = "none")

p.acimf <- ggplot(data =ACI_MF.hr.av, aes(x=as.numeric(Hour), y=MF_ACI)) + geom_line(aes(color=as.character(Site))) + xlab("Hour") + ylab ("MF_ACI") + scale_color_brewer(palette = "Set1") + ggtitle("Averaged MF ACI")

#Horizontal graph
#splbb.h <- plot_grid(p.splbb17, p.splbb18, labels = c("2017", "2018"), align = "h")
#splbb.h

acimf.v <- plot_grid(p.acimf17, p.acimf18, labels = c("2017", "2018"), label_x = .5, nrow = 2 )

acimf.v
p.acimf
```

### Boxplots
Distribution of ACI at all frequencies and sites - averaged by hour
```{r aci bp, echo=FALSE}
#Boxplot

p.acibb.bp <- ggplot(data = ACI_BB.hr.long, aes(y = Broadband_ACI, x = Site, fill = Year)) + geom_boxplot() + ylab("ACI")
p.acihf.bp <- ggplot(data = ACI_HF.hr.long, aes(y = HF_ACI, x = Site, fill = Year)) + geom_boxplot() + ylab("ACI")
p.acimf.bp <- ggplot(data = ACI_MF.hr.long, aes(y = MF_ACI, x = Site, fill = Year)) + geom_boxplot() + ylab("ACI")

p.aci.bp <- plot_grid(p.acibb.bp, p.acihf.bp, p.acimf.bp, labels = c("Broadband", "High Frequency", "Mid Frequency"), nrow = 3, align = "v", label_x = .4)

p.aci.bp
```

##Fish Sounds

###Total Knocks - Hourly
Total number of knocks is the sum total of a 5 minute recording from the beginning of each hour
```{r tkh, echo=FALSE}

##reordering levels for the legend
FC.sep$Hour <- factor(FC.sep$Hour, levels = c("3", "9", "15", "21"))
FC.sep17$Hour <- factor(FC.sep17$Hour, levels = c("3", "9", "15", "21"))
FC.sep18$Hour <- factor(FC.sep18$Hour, levels = c("3", "9", "15", "21"))

fcALL.bp <- ggplot(data = FC.sep, aes(y = Tot_Knocks, x = Site, fill = Hour)) + geom_boxplot() + ylab("# of Knocks") + theme(legend.position = "none", axis.title.x = element_blank())

fc17.bp <- ggplot(data = FC.sep17, aes(y = Tot_Knocks, x = Site, fill = Hour)) + geom_boxplot() + ylab("# of Knocks") + theme (legend.position = "none", axis.title.x = element_blank())

fc18.bp <- ggplot(data = FC.sep18, aes(y = Tot_Knocks, x = Site, fill = Hour)) + geom_boxplot() + ylab("# of Knocks") + theme (legend.position = "none")

p.fc.bp <- plot_grid(fcALL.bp, fc17.bp, fc18.bp, labels = c("All Years", "2017", "2018"), nrow = 3, align = "v", label_x = .5)

p.fc.bp

```

The 4 box plots in each site represent each time frame, 3 am, 9 am, 3 pm, and 9 pm - in that order

###Total Knocks - Daily
Total number of knocks summing all 4 samples to get a daily amount - to compare sites
```{r tkd, echo=FALSE}

fCALL.bp <- ggplot(data = FC.sd, aes(x = Site, y = Tot_Knocks)) + geom_boxplot() + ylab("# of Knocks") + theme (axis.title.x = element_blank())

fC17.bp <- ggplot(data = FC.sd17, aes(y = Tot_Knocks, x = Site)) + geom_boxplot() + ylab("# of Knocks") + theme (legend.position = "none", axis.title.x = element_blank())

fC18.bp <- ggplot(data = FC.sd18, aes(y = Tot_Knocks, x = Site)) + geom_boxplot() + ylab("# of Knocks")

p.fC.bp <- plot_grid(fCALL.bp, fC17.bp, fC18.bp, labels = c("All Years", "2017", "2018"), nrow = 3, align = "v", label_x = .5)

p.fC.bp

```

###Long Calls - Hourly
Total number of long calls is the sum total of a 5 minute recording from the beginning of each hour
```{r tlch, echo=FALSE}

##reordering levels for the legend
flCALL.bp <- ggplot(data = FC.sep, aes(y = Num_L_calls, x = Site, fill = Hour)) + geom_boxplot() + ylab("# of Knocks") + theme(legend.position = "none", axis.title.x = element_blank())

flC17.bp <- ggplot(data = FC.sep17, aes(y = Num_L_calls, x = Site, fill = Hour)) + geom_boxplot() + ylab("# of Knocks") + theme (legend.position = "none", axis.title.x = element_blank())

flC18.bp <- ggplot(data = FC.sep18, aes(y = Num_L_calls, x = Site, fill = Hour)) + geom_boxplot() + ylab("# of Knocks") + theme (legend.position = "none")

p.flC.bp <- plot_grid(flCALL.bp, flC17.bp, flC18.bp, labels = c("All Years", "2017", "2018"), nrow = 3, align = "v", label_x = .5)

p.flC.bp

```

The 4 box plots in each site represent each time frame, 3 am, 9 am, 3 pm, and 9 pm - in that order

###Long Calls - Daily
Total long calls summing all 4 samples to get a daily amount - to compare sites
```{r tlcd, echo=FALSE}

flcall.bp <- ggplot(data = FC.sd, aes(x = Site, y = Num_L_calls)) + geom_boxplot() + ylab("# LC") + theme (axis.title.x = element_blank())

flc17.bp <- ggplot(data = FC.sd17, aes(y = Num_L_calls, x = Site)) + geom_boxplot() + ylab("# LC") + theme (legend.position = "none", axis.title.x = element_blank())

flc18.bp <- ggplot(data = FC.sd18, aes(y = Num_L_calls, x = Site)) + geom_boxplot() + ylab("# LC")

p.flc.bp <- plot_grid(flcall.bp, flc17.bp, flc18.bp, labels = c("All Years", "2017", "2018"), nrow = 3, align = "v", label_x = .5)

p.flc.bp

```

#Fish Abundance

**Fish Abundance** is the sum total of fish at that site at each observation that year, averages are made within sites within years when multiple UVC were made.  However, all data has been plotted in addition to any averages to ensure that we know where the averages come from.

##Sum Fish abundance - summed to each UVC
```{r fish abundance, echo = FALSE}
FA.ab17 <- ggplot(ki.acab17, aes(x = Site, y = Number, fill = MD)) + geom_bar(stat = "identity", position = "dodge")+  geom_text(aes(label=Number), position = position_dodge(1), vjust = -.5) + scale_fill_brewer(palette = "Paired") + theme(axis.title.x = element_blank(), legend.position = "none") + ylim (0,15000)

FA.ab18 <- ggplot(ki.acab18, aes(x = Site, y = Number, fill = MD)) + geom_bar(stat = "identity", position = "dodge")+  geom_text(aes(label=Number), position = position_dodge(1), vjust = -.5) + scale_fill_brewer(palette = "Paired") + ylim(0, 15000) + theme (legend.position = "none")

p.FA.ab <- plot_grid(FA.ab17, FA.ab18, labels = c("2017", "2018"), nrow = 2, align = "v", label_x = .5 )

p.FA.ab
```



##Average Fish abundance
Fish Abundance - Averaged within years and then across years at all sites
```{r fish average, echo = FALSE}
FA.av17 <- ggplot(ki.acav17, aes(x = Site, y = Number)) + geom_bar(stat = "identity", position = "dodge")+  geom_text(aes(label=Number), position = position_dodge(1), vjust = -.5) + scale_fill_brewer(palette = "Set1") + theme(axis.title.x = element_blank(), legend.position = "none") + ylim (0,15000)

FA.av18 <- ggplot(ki.acav18, aes(x = Site, y = Number)) + geom_bar(stat = "identity", position = "dodge")+  geom_text(aes(label=Number), position = position_dodge(1), vjust = -.5) + scale_fill_brewer(palette = "Paired") + ylim(0, 15000) + theme (legend.position = "none")

FA.av <- ggplot(ki.acav, aes(x = Site, y = Number)) + geom_bar(stat = "identity", position = "dodge")+  geom_text(aes(label=Number), position = position_dodge(1), vjust = -.5) + scale_fill_brewer(palette = "Paired") + ylim(0, 15000) + theme (legend.position = "none")


p.FA.av <- plot_grid(FA.av17, FA.av18, FA.av, labels = c("2017", "2018", "All Years"), nrow = 3, align = "v", label_x = .5 )

p.FA.av
```
#Boat Visitations

**Boat Visitations** is the sum total number of boats detected visiting each site over their entire time deployed

*Note* this is ONLY the 2018 data

Boat Visitation Data for 2018 at each site
```{r boats, echo = FALSE}
#making site a character
BV.sum$Site <- as.character(BV.sum$Site)
boats <- ggplot(BV.sum, aes(x = Site, y = Visitations)) + geom_bar(stat = "identity", position = "dodge")+  geom_text(aes(label=Visitations), position = position_dodge(1), vjust = -.5) + scale_fill_brewer(palette = "Set1") + ggtitle ("Boat Visitations in 2018") + ylim(0,130)

boats
```


#Combined Model
**Combined Model** All variables are matched to the files that were used for Fish call counts (3:00, 9:00, 15:00, 21:00)

##Box Plots

```{r combined model, echo = FALSE}
colnames(AC.DF1)

#reordering hour so that it is in chronological order
AC.DF1$Hour <- factor(AC.DF1$Hour, levels = c("3", "9", "15", "21"))

#Bar graphs with Hour as the X variable
SPL_BBp <- ggplot(data = AC.DF1, aes(y = SPL_BB, x = Hour, fill = Year)) + geom_boxplot() + ylab("BB_SPL") + xlab("Hour") + theme(legend.position = "none")

SPL_HFp <- ggplot(data = AC.DF1, aes(y = SPL_HF, x = Hour, fill = Year)) + geom_boxplot() + ylab("HF_SPL") + xlab("Hour") + theme(legend.position = "none")

SPL_MFp <- ggplot(data = AC.DF1, aes(y = SPL_Midrange, x = Hour, fill = Year)) + geom_boxplot() + ylab("MF_SPL") + xlab("Hour")

Tot_Kp <- ggplot(data = AC.DF1, aes(y = Tot_Knocks, x = Hour, fill = Year)) + geom_boxplot() + ylab("Knocks") + xlab("Hour") + theme(legend.position = "none")

LCp <- ggplot(data = AC.DF1, aes(y = Num_L_calls, x = Hour, fill = Year)) + geom_boxplot() + ylab("Long Calls") + xlab("Hour") + theme(legend.position = "none")

Herbp <- ggplot(data = AC.DF1, aes(y = Num_Herbivory, x = Hour, fill = Year)) + geom_boxplot() + ylab("Herbivory") + xlab("Hour") + theme(legend.position = "none")

Snapp <- ggplot(data = AC.DF1, aes(y = Snaps, x = Hour, fill = Year)) + geom_boxplot() + ylab("Snaps") + xlab("Hour")

hour.f_bp <- plot_grid(SPL_BBp, SPL_HFp, SPL_MFp, nrow = 2, ncol = 2)

#pdf(file="../Figures/Hour_Metrics.pdf", width = 11, height = 7)
hour.f_bp
#dev.off()

hour_bp <- plot_grid(Tot_Kp, LCp, Herbp, Snapp, nrow = 2, ncol = 2)

#pdf(file="../Figures/Hour_Counts.pdf", width = 11, height = 7)
hour_bp
#dev.off()

hour.comp <- plot_grid(SPL_MFp, Tot_Kp, SPL_HFp, Snapp, nrow = 2, ncol =2)

#pdf(file="../Figures/Hour_Compare.pdf", width = 11, height = 7)
hour.comp
#dev.off()

#Bar graphs with Site as the x variable

# making site a factor
AC.DF1$Site <- as.character(AC.DF1$Site)

SPL_BBp1 <- ggplot(data = AC.DF1, aes(y = SPL_BB, x = Site, fill = Year)) + geom_boxplot() + ylab("BB_SPL") + xlab("Site") + theme(legend.position = "none")

SPL_HFp1 <- ggplot(data = AC.DF1, aes(y = SPL_HF, x = Site, fill = Year)) + geom_boxplot() + ylab("HF_SPL") + xlab("Site") + theme(legend.position = "none")

SPL_MFp1 <- ggplot(data = AC.DF1, aes(y = SPL_Midrange, x = Site, fill = Year)) + geom_boxplot() + ylab("MF_SPL") + xlab("Site")

Tot_Kp1 <- ggplot(data = AC.DF1, aes(y = Tot_Knocks, x = Site, fill = Year)) + geom_boxplot() + ylab("Knocks") + xlab("Site") + theme(legend.position = "none")

LCp1 <- ggplot(data = AC.DF1, aes(y = Num_L_calls, x = Site, fill = Year)) + geom_boxplot() + ylab("Long Calls") + xlab("Site") + theme(legend.position = "none")

Herbp1 <- ggplot(data = AC.DF1, aes(y = Num_Herbivory, x = Site, fill = Year)) + geom_boxplot() + ylab("Herbivory") + xlab("Site") + theme(legend.position = "none")

Snapp1 <- ggplot(data = AC.DF1, aes(y = Snaps, x = Site, fill = Year)) + geom_boxplot() + ylab("Snaps") + xlab("Site")

site.f_bp <- plot_grid(SPL_BBp1, SPL_HFp1, SPL_MFp1, nrow = 2, ncol = 2)

#pdf(file="../Figures/Site_Metrics.pdf", width = 11, height = 7)
site.f_bp
#dev.off()

site_bp <- plot_grid(Tot_Kp1, LCp1, Herbp1,Snapp1, nrow = 2, ncol = 2)

#pdf(file="../Figures/Site_Counts.pdf", width = 11, height = 7)
site_bp
#dev.off()

site.comp <- plot_grid(SPL_MFp1, Tot_Kp1, SPL_HFp1, Snapp1, nrow = 2, ncol = 2)

#pdf(file="../Figures/Site_Compare.pdf", width = 11, height = 7)
site.comp
#dev.off()
```

##Distributions

```{r histogram, echo = FALSE}
#plotting count histogram

Count.hist <- ggplot(data = AC.DF1, aes(AC.DF1$Tot_Knocks)) + geom_histogram()
Herb.hist <- ggplot(data = AC.DF1, aes(AC.DF1$Num_Herbivory)) + geom_histogram()
LC.hist <- ggplot(data = AC.DF1, aes(AC.DF1$Num_L_calls)) + geom_histogram()


hist.p <- plot_grid(Count.hist, Herb.hist, LC.hist, nrow = 1, ncol = 3)
hist.p

#plotting distributions of SPL response variables
MF.hist <- ggplot(data = AC.DF1, aes(AC.DF1$SPL_Midrange)) + geom_histogram()
BB.hist <- ggplot(data = AC.DF1, aes(AC.DF1$SPL_BB)) + geom_histogram()
HF.hist <- ggplot(data = AC.DF1, aes(AC.DF1$SPL_HF)) + geom_histogram()

hist1.p <- plot_grid(MF.hist, BB.hist, HF.hist, nrow = 1, ncol = 3)
hist1.p

#plotting distributions of ACI response variables
MF.hist1 <- ggplot(data = AC.DF1, aes(AC.DF1$ACI_Midrange)) + geom_histogram()
BB.hist1 <- ggplot(data = AC.DF1, aes(AC.DF1$ACI_BB)) + geom_histogram()
HF.hist1 <- ggplot(data = AC.DF1, aes(AC.DF1$ACI_HF)) + geom_histogram()

hist2.p <- plot_grid(MF.hist1, BB.hist1, HF.hist1, nrow = 1, ncol = 3)
hist2.p

```

##Plotting regressions

```{r regression, echo = FALSE}
#plotting total knocks against midrange SPL
GLM1 <- ggplot(AC.DF1, aes(Tot_Knocks, SPL_Midrange)) + geom_point() + geom_smooth(method = "glm")

GLM2 <- ggplot(AC.DF1, aes(Snaps, SPL_HF)) + geom_point() + geom_smooth(method = "glm")


GLM3 <- ggplot(AC.DF1, aes(Snaps, SPL_BB)) + geom_point() + geom_smooth(method = "glm")

GLM4 <- ggplot(AC.DF1, aes(Tot_Knocks, ACI_Midrange)) + geom_point() + geom_smooth(method = "glm")

glm.p <- plot_grid(GLM1, GLM2, GLM3, GLM4, nrow = 1, ncol = 4)
glm.p
```
