---
title: "Acoustic_2019_Explore2"
author: "Sean Dimoff"
date: "October 9, 2019"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
---

```{r setup, include=FALSE}
library(ggplot2)
library(cowplot)
library(rmarkdown)
library(knitr)
library(RColorBrewer)
library(GGally)
library(mctest)
library(usdm)
library(hms)
library(dplyr)

##loading in the ACI/SPL data - wide form

#hourdata
#load("../Raw_Data/ACI_BB17hr.Rdata")
#load("../Raw_Data/ACI_BB18hr.Rdata")
#load("../Raw_Data/ACI_HF17hr.Rdata")
#load("../Raw_Data/ACI_HF18hr.Rdata")
#load("../Raw_Data/ACI_MF17hr.Rdata")
#load("../Raw_Data/ACI_MF18hr.Rdata")
#
#load("../Raw_Data/SPL_BB17hr.Rdata")
#load("../Raw_Data/SPL_BB18hr.Rdata")
#load("../Raw_Data/SPL_HF17hr.Rdata")
#load("../Raw_Data/SPL_HF18hr.Rdata")
#load("../Raw_Data/SPL_MF17hr.Rdata")
#load("../Raw_Data/SPL_MF18hr.Rdata")

#All time data
load("../Raw_Data/SPL_BB17.Rdata")
load("../Raw_Data/SPL_BB18.Rdata")

load("../Raw_Data/SPLBB17long.Rdata")
load("../Raw_Data/SPLBB18long.Rdata")

load("../Raw_Data/SPLHF17long.Rdata")
load("../Raw_Data/SPLHF18long.Rdata")

load("../Raw_Data/SPLMF17long.Rdata")
load("../Raw_Data/SPLMF18long.Rdata")

load("../Raw_Data/SPLHFlong.Rdata")
load("../Raw_Data/SPLMFlong.Rdata")



#combined SPL and HF dataframes
load("../Raw_Data/Snap.HF17.Rdata")
load("../Raw_Data/Snap.HF18.Rdata")

load("../Raw_Data/Snap.HF.Rdata")



#daydata
#load("../Raw_Data/ACI_BB17day.Rdata")
#load("../Raw_Data/ACI_BB18day.Rdata")
#load("../Raw_Data/ACI_HF17day.Rdata")
#load("../Raw_Data/ACI_HF18day.Rdata")
#load("../Raw_Data/ACI_MF17day.Rdata")
#load("../Raw_Data/ACI_MF18day.Rdata")
#
#load("../Raw_Data/SPL_BB17day.Rdata")
#load("../Raw_Data/SPL_BB18day.Rdata")
#load("../Raw_Data/SPL_HF17day.Rdata")
#load("../Raw_Data/SPL_HF18day.Rdata")
#load("../Raw_Data/SPL_MF17day.Rdata")
#load("../Raw_Data/SPL_MF18day.Rdata")

#loading ACI/SPL long data for boxplots
#ACI
#load("../Raw_Data/ACI_BB17hrlong.Rdata")
#load("../Raw_Data/ACI_HF17hrlong.Rdata")
#load("../Raw_Data/ACI_MF17hrlong.Rdata")
#load("../Raw_Data/ACI_BB18hrlong.Rdata")
#load("../Raw_Data/ACI_HF18hrlong.Rdata")
#load("../Raw_Data/ACI_MF18hrlong.Rdata")
#
#load("../Raw_Data/ACI_MFhrlong.Rdata")
#load("../Raw_Data/ACI_HFhrlong.Rdata")
#load("../Raw_Data/ACI_BBhrlong.Rdata")
#
#load("../Raw_Data/ACI_BBhr_av.Rdata")
#load("../Raw_Data/ACI_HFhr_av.Rdata")
#load("../Raw_Data/ACI_MFhr_av.Rdata")
#
####making year a character
#ACI_BB.hr.long$Year <- as.character(ACI_BB.hr.long$Year)
#ACI_HF.hr.long$Year <- as.character(ACI_HF.hr.long$Year)
#ACI_MF.hr.long$Year <- as.character(ACI_MF.hr.long$Year)
#
###SPL
#load("../Raw_Data/SPL_BB17hrlong.Rdata")
#load("../Raw_Data/SPL_HF17hrlong.Rdata")
#load("../Raw_Data/SPL_MF17hrlong.Rdata")
#load("../Raw_Data/SPL_BB18hrlong.Rdata")
#load("../Raw_Data/SPL_HF18hrlong.Rdata")
#load("../Raw_Data/SPL_MF18hrlong.Rdata")
#
#load("../Raw_Data/SPL_MFhrlong.Rdata")
#load("../Raw_Data/SPL_HFhrlong.Rdata")
#load("../Raw_Data/SPL_BBhrlong.Rdata")
#
#load("../Raw_Data/SPL_BBhr_av.Rdata")
#load("../Raw_Data/SPL_HFhr_av.Rdata")
#load("../Raw_Data/SPL_MFhr_av.Rdata")
#
###making year a character
#SPL_BB.hr.long$Year <- as.character(SPL_BB.hr.long$Year)
#SPL_HF.hr.long$Year <- as.character(SPL_HF.hr.long$Year)
#SPL_MF.hr.long$Year <- as.character(SPL_MF.hr.long$Year)
#
##loading in fish call count data
#load("../Raw_Data/FC.05hr.Rdata")
#load("../Raw_Data/FC.08hr.Rdata")
#load("../Raw_Data/FC.32hr.Rdata")
#load("../Raw_Data/FC.35hr.Rdata")
#load("../Raw_Data/FC.40hr.Rdata")
#
#load("../Raw_Data/FC.CallperDayALL.Rdata")
#load("../Raw_Data/FC.CallperDay17.Rdata")
#load("../Raw_Data/FC.CallperDay18.Rdata")
#
#load("../Raw_Data/FC.CallperHourALL.Rdata")
#load("../Raw_Data/FC.CallperHour17.Rdata")
#load("../Raw_Data/FC.CallperHour18.Rdata")

#loading in total dataframe
#load("../Raw_Data/AC.DF.Rdata")




##loading in Boat visitation data
load("../Raw_Data/BV.all.Rdata")
load("../Raw_Data/BV.sum.Rdata")





##loading in lunar phase data
#load("../Raw_Data/LunarPhase2017.Rdata")
#load("../Raw_Data/LunarPhase2018.Rdata")


##loading in fish data
#load("../Raw_Data/ki_fishabundance.Rdata")
#load("../Raw_Data/ki_fishabundance17.Rdata")
#load("../Raw_Data/ki_fishabundance18.Rdata")
#
#load("../Raw_Data/ki_fishaverage.Rdata")
#load("../Raw_Data/ki_fishaverage17.Rdata")
#load("../Raw_Data/ki_fishaverage18.Rdata")


##loading in the full dataframe with all data
load("../Raw_Data/AC.DF.Rdata")
load("../Raw_Data/AC.DF1.Rdata")



```
**Exploratory Plots for 2017-2018 Acoustic/Fish Data**

**Purpose** To explore the Acoustic data gathered in 2017 and 2018 to expose important trends between sites, diurnal patterns, fish abundance, lunar phase, and coral reef acoustics.

#Time-Series Acoustics
**Acoustics Breakdown** All acoustic metrics (SPL and ACI) are broken down into 3 frequency bands: Broadband (All frequencies), High Frequency (Frequencies between 1 kHz - 22 kHz), and Mid Frequency (Frequencies between 160 Hz and 1 kHz)

*Note* 2017 had a 10 minute duty cycle with 5 minutes recording while 2018 had a 15 minute duty cycle with 5 minutes recording, so the number of files averages differs between years

##Frequency-Band Breakdowns

### High Frequency
Plots of high frequency patterns, notice diurnal patterns with highest SPL at night and lowest during the day (this is shown in the literature), also notice the clear splits by site.

```{r hf spl no av, echo = FALSE}
#2017

#converting site to character
SPLHF17.long$Site <- as.character(SPLHF17.long$Site)

#comparing between sites for entire deployment
full.SPLHF17 <- ggplot(data =SPLHF17.long, aes(x=datetime, y = SPL_HF)) + 
  geom_point(aes(color = Site)) + geom_smooth(aes(color = Site), method = "loess") +
  theme(axis.text.x = element_text(angle = 90)) + scale_x_datetime(date_breaks = "1 day") + theme(axis.text.x = element_text(angle = 90)) + ggtitle("HF SPL total deployment, 2017")

#converting date to character
SPLHF17.long$Date <- as.character(SPLHF17.long$Date)

#converting site to character
SPLHF17.long$Site <- as.character(SPLHF17.long$Site)

#comparing between sites for 1 day
day.SPLHF17 <- ggplot(data = SPLHF17.long, aes(x= Time, y = SPL_HF)) + geom_point(aes(color = Site)) + theme(axis.text.x = element_text(angle = 90)) + geom_smooth(aes(color = Site), method = "loess") + ggtitle("HF SPL diurnal patterns, 2017")


#2018
#converting site to character
SPLHF18.long$Site <- as.character(SPLHF18.long$Site)

#comparing between sites for entire deployment
full.SPLHF18 <- ggplot(data =SPLHF18.long, aes(x=datetime, y = SPL_HF)) + 
  geom_point(aes(color = Site)) + geom_smooth(aes(color = Site), method = "loess") +
  theme(axis.text.x = element_text(angle = 90)) + scale_x_datetime(date_breaks = "1 day") + theme(axis.text.x = element_text(angle = 90)) + ggtitle("HF SPL total deployment, 2018")

#converting date to character
SPLHF18.long$Date <- as.character(SPLHF18.long$Date)

#converting site to character
SPLHF18.long$Site <- as.character(SPLHF18.long$Site)

#comparing between sites for 1 day
day.SPLHF18 <- ggplot(data = SPLHF18.long, aes(x= Time, y = SPL_HF)) + geom_point(aes(color = Site)) + theme(axis.text.x = element_text(angle = 90)) + geom_smooth(aes(color = Site), method = "loess") + ggtitle("HF SPL diurnal patterns, 2018")

full.SPLHF17
full.SPLHF18
day.SPLHF17
day.SPLHF18

#combined

#converting site to character
SPLHF.long$Site <- as.character(SPLHF.long$Site)

day.SPLHF <- ggplot(data = SPLHF.long, aes(x= Time, y = SPL_HF)) + geom_point(aes(color = Site)) + theme(axis.text.x = element_text(angle = 90)) + geom_smooth(aes(color = Site), method = "loess") + ggtitle("HF SPL diurnal patterns, combined years")

day.SPLHF
```

Notice, site 35 seems to have switched position between 2017 and 2018 but all of the other sites seem to be staying more or less in the same spot

- I wonder if this has to do with macroalgal cover changes between 2017 and 2018


### Mid Frequency
Plots of mid frequency patterns, notice opposite diurnal patterns with highest SPL during the day and lowest at night, also notice the clear splits by site.

```{r mf spl no av, echo = FALSE}
#2017

#converting site to character
SPLMF17.long$Site <- as.character(SPLMF17.long$Site)

#comparing between sites for entire deployment
full.SPLMF17 <- ggplot(data =SPLMF17.long, aes(x=datetime, y = SPL_MF)) + 
  geom_point(aes(color = Site)) + geom_smooth(aes(color = Site), method = "loess") +
  theme(axis.text.x = element_text(angle = 90)) + scale_x_datetime(date_breaks = "1 day") + theme(axis.text.x = element_text(angle = 90)) + ggtitle("MF SPL total deployment, 2017")

#converting date to character
SPLMF17.long$Date <- as.character(SPLMF17.long$Date)

#converting site to character
SPLMF17.long$Site <- as.character(SPLMF17.long$Site)

#comparing between sites for 1 day
day.SPLMF17 <- ggplot(data = SPLMF17.long, aes(x= Time, y = SPL_MF)) + geom_point(aes(color = Site)) + theme(axis.text.x = element_text(angle = 90)) + geom_smooth(aes(color = Site), method = "loess") + ggtitle("MF SPL diurnal patterns, 2017")



#2018
#converting site to character
SPLMF18.long$Site <- as.character(SPLMF18.long$Site)

#comparing between sites for entire deployment
full.SPLMF18 <- ggplot(data =SPLMF18.long, aes(x=datetime, y = SPL_MF)) + 
  geom_point(aes(color = Site)) + geom_smooth(aes(color = Site), method = "loess") +
  theme(axis.text.x = element_text(angle = 90)) + scale_x_datetime(date_breaks = "1 day") + theme(axis.text.x = element_text(angle = 90)) + ggtitle("MF SPL total deployment, 2018")


#converting date to character
SPLMF18.long$Date <- as.character(SPLMF18.long$Date)

#converting site to character
SPLMF18.long$Site <- as.character(SPLMF18.long$Site)

#comparing between sites for 1 day
day.SPLMF18 <- ggplot(data = SPLMF18.long, aes(x= Time, y = SPL_MF)) + geom_point(aes(color = Site)) + theme(axis.text.x = element_text(angle = 90)) + geom_smooth(aes(color = Site), method = "loess") + ggtitle("MF SPL diurnal patterns, 2018")


full.SPLMF17
full.SPLMF18
day.SPLMF17
day.SPLMF18

#combined model
#comparing between sites for 1 day
#making site a character
SPLMF.long$Site <- as.character(SPLMF.long$Site)

day.SPLMF <- ggplot(data = SPLMF.long, aes(x= Time, y = SPL_MF)) + geom_point(aes(color = Site)) + theme(axis.text.x = element_text(angle = 90))

day.SPLMF + ggtitle("MF SPL diurnal patterns, combined years")

#plotting HF and MF on same plot each year

```

Also, notice that 35 does a similar switch in Mid-frequency, going from the bottom in 2017 to the top in 2018

## Combo Plots
```{r combo hf mf, echo = FALSE}
#creating combined dataframe
SPL.both <- cbind(SPLMF17.long, SPLHF17.long$SPL_HF)

SPL.both18 <- cbind(SPLMF18.long, SPLHF18.long$SPL_HF)

SPL.both.b <- cbind(SPLMF.long, SPLHF.long$SPL_HF)

#renaming columns
names(SPL.both) <- c("Date", "Time", "SPL_MF", "Site", "datetime", "SPL_HF")
names(SPL.both18) <- c("Date", "Time", "SPL_MF", "Site", "datetime", "SPL_HF")
names(SPL.both.b) <- c("Date", "Time", "SPL_MF", "Site", "datetime", "SPL_HF")
#comparing between sites for entire deployment
full.SPL <- ggplot(data =SPL.both, aes(x=datetime)) + 
  geom_point(aes(y = SPL_MF, color = Site)) + geom_point(aes(y = SPL_HF, color = Site)) +
  theme(axis.text.x = element_text(angle = 90)) + scale_x_datetime(date_breaks = "1 day") + theme(axis.text.x = element_text(angle = 90)) + ggtitle("MF and HF SPL total deployment, 2017")
full.SPL

#comparing between sites for 1 day
day.SPL <- ggplot(data = SPL.both, aes(x= Time)) + geom_point(aes(y = SPL_MF, color = Site)) + geom_point(aes(y = SPL_HF, color = Site)) + theme(axis.text.x = element_text(angle = 90)) + ylab("SPL")+ ggtitle("MF and HF SPL diurnal pattern, 2017")
day.SPL

#comparing between sites for entire deployment
full.SPL18 <- ggplot(data =SPL.both18, aes(x=datetime)) + 
  geom_point(aes(y = SPL_MF, color = Site)) + geom_point(aes(y = SPL_HF, color = Site)) +
  theme(axis.text.x = element_text(angle = 90)) + scale_x_datetime(date_breaks = "1 day") + theme(axis.text.x = element_text(angle = 90)) + ggtitle("MF and HF SPL total deployment, 2018")
full.SPL18

#comparing between sites for 1 day
day.SPL18 <- ggplot(data = SPL.both18, aes(x= Time)) + geom_point(aes(y = SPL_MF, color = Site)) + geom_point(aes(y = SPL_HF, color = Site)) + theme(axis.text.x = element_text(angle = 90)) + ylab("SPL")+ ggtitle("MF and HF SPL diurnal pattern, 2018")
day.SPL18

#comparing between sites for 1 day
day.SPL.both <- ggplot(data = SPL.both.b, aes(x= Time)) + geom_point(aes(y = SPL_MF, color = Site)) + geom_point(aes(y = SPL_HF, color = Site)) + theme(axis.text.x = element_text(angle = 90)) + ylab("SPL")+ ggtitle("MF and HF SPL diurnal pattern, combined years")
day.SPL.both

```




#Validations
**Combined Model** All variables are matched to the files that were used for Fish call counts (3:00, 9:00, 15:00, 21:00)

##Box Plots

```{r combined model, echo = FALSE}
#colnames(AC.DF1)
#
##reordering hour so that it is in chronological order
#AC.DF1$Hour <- factor(AC.DF1$Hour, levels = c("3", "9", "15", "21"))
#
##Box graphs with Hour as the X variable
#
#SPL_HFp <- ggplot(data = AC.DF1, aes(y = SPL_HF, x = Hour, fill = Year)) + geom_boxplot() + ylab("HF_SPL") + xlab("Hour") + theme(legend.position = "none")
#
#SPL_MFp <- ggplot(data = AC.DF1, aes(y = SPL_Midrange, x = Hour, fill = Year)) + geom_boxplot() + ylab("MF_SPL") + xlab("Hour") + theme(legend.position = #"none")
#
#Tot_Kp <- ggplot(data = AC.DF1, aes(y = Tot_Knocks, x = Hour, fill = Year)) + geom_boxplot() + ylab("Knocks") + xlab("Hour") + theme(legend.position = "none")
#
#LCp <- ggplot(data = AC.DF1, aes(y = Num_L_calls, x = Hour, fill = Year)) + geom_boxplot() + ylab("Long Calls") + xlab("Hour") + theme(legend.position = #"none")
#
#Herbp <- ggplot(data = AC.DF1, aes(y = Num_Herbivory, x = Hour, fill = Year)) + geom_boxplot() + ylab("Herbivory") + xlab("Hour") + theme(legend.position = #"none")
#
#Snapp <- ggplot(data = AC.DF1, aes(y = Snaps, x = Hour, fill = Year)) + geom_boxplot() + ylab("Snaps") + xlab("Hour") + theme(legend.position = "none")
#
#hour.f_bp <- plot_grid( SPL_HFp, SPL_MFp, nrow = 1, ncol = 2)
#
##pdf(file="../Figures/Hour_Metrics.pdf", width = 11, height = 7)
#hour.f_bp
##dev.off()
#
#hour_bp <- plot_grid(Tot_Kp, LCp, Herbp, Snapp, nrow = 2, ncol = 2)
#
##pdf(file="../Figures/Hour_Counts.pdf", width = 11, height = 7)
#hour_bp
##dev.off()
#
#hour.comp <- plot_grid(SPL_MFp, Tot_Kp, SPL_HFp, Snapp, nrow = 2, ncol =2)
#
##pdf(file="../Figures/Hour_Compare.pdf", width = 11, height = 7)
#hour.comp
##dev.off()
#
##Box graphs with Site as the x variable
#
## making site a factor
#AC.DF1$Site <- as.character(AC.DF1$Site)
#
#SPL_HFp1 <- ggplot(data = AC.DF1, aes(y = SPL_HF, x = Site, fill = Year)) + geom_boxplot() + ylab("HF_SPL") + xlab("Site") + theme(legend.position = "none")
#
#SPL_MFp1 <- ggplot(data = AC.DF1, aes(y = SPL_Midrange, x = Site, fill = Year)) + geom_boxplot() + ylab("MF_SPL") + xlab("Site") + theme(legend.position = #"none")
#
#Tot_Kp1 <- ggplot(data = AC.DF1, aes(y = Tot_Knocks, x = Site, fill = Year)) + geom_boxplot() + ylab("Knocks") + xlab("Site") + theme(legend.position = #"none")
#
#LCp1 <- ggplot(data = AC.DF1, aes(y = Num_L_calls, x = Site, fill = Year)) + geom_boxplot() + ylab("Long Calls") + xlab("Site") + theme(legend.position = #"none")
#
#Herbp1 <- ggplot(data = AC.DF1, aes(y = Num_Herbivory, x = Site, fill = Year)) + geom_boxplot() + ylab("Herbivory") + xlab("Site") + theme(legend.position = #"none")
#
#Snapp1 <- ggplot(data = AC.DF1, aes(y = Snaps, x = Site, fill = Year)) + geom_boxplot() + ylab("Snaps") + xlab("Site") + theme(legend.position = "none")
#
#site.f_bp <- plot_grid(SPL_HFp1, SPL_MFp1, nrow = 1, ncol = 2)
#
##pdf(file="../Figures/Site_Metrics.pdf", width = 11, height = 7)
#site.f_bp
##dev.off()
#
#site_bp <- plot_grid(Tot_Kp1, LCp1, Herbp1,Snapp1, nrow = 2, ncol = 2)
#
##pdf(file="../Figures/Site_Counts.pdf", width = 11, height = 7)
#site_bp
##dev.off()
#
#
#site.comp <- plot_grid(SPL_MFp1, Tot_Kp1, SPL_HFp1, Snapp1, nrow = 2, ncol = 2)
#
##pdf(file="../Figures/Site_Compare.pdf", width = 11, height = 7)
#site.comp
##dev.off()
#
#site.spl_bp <- plot_grid(Tot_Kp1, SPL_MFp1, LCp1, SPL_HFp1, Snapp1 , nrow = 3, ncol = 2)
#
##pdf(file="../Figures/Site_Compare.SPL.pdf", width = 11, height = 7)
#site.spl_bp
##dev.off()
#
#
#### ACI Plot ###
#
#Tot_Kp2 <- ggplot(data = AC.DF1, aes(y = Tot_Knocks, x = Site, fill = Year)) + geom_boxplot() + ylab("Knocks") + xlab("Site") + theme(legend.position = #"none")
#
#LCp2 <- ggplot(data = AC.DF1, aes(y = Num_L_calls, x = Site, fill = Year)) + geom_boxplot() + ylab("Long Calls") + xlab("Site") + theme(legend.position = #"none")
#
#Snapp2 <- ggplot(data = AC.DF1, aes(y = Snaps, x = Site, fill = Year)) + geom_boxplot() + ylab("Snaps") + xlab("Site") + theme(legend.position = "none")
#
#ACI_MFp <- ggplot(data = AC.DF1, aes(y = ACI_Midrange, x = Site, fill = Year)) + geom_boxplot() + ylab("MF_ACI") + xlab("Site") + theme(legend.position = #"none")
#
#ACI_HFp <- ggplot(data = AC.DF1, aes(y = ACI_HF, x = Site, fill = Year)) + geom_boxplot() + ylab("HF_ACI") + xlab("Site") + theme(legend.position = "none")
#
#ACI_BBp <- ggplot(data = AC.DF1, aes(y = ACI_BB, x = Site, fill = Year)) + geom_boxplot() + ylab("BB_ACI") + xlab("Site") + theme(legend.position = "none")
#
#site.aci_bp <- plot_grid(Tot_Kp2, ACI_MFp, LCp2, ACI_HFp, Snapp2, ACI_BBp , nrow = 2, ncol = 3)
#
##pdf(file="../Figures/Site_Compare.ACI.pdf", width = 11, height = 7)
#site.aci_bp
##dev.off()
```

##Confidence Intervals
```{r CI, echo = FALSE}

##Knocks

#taking average and calculating confidence intervals for sites
knock.av <- aggregate(Tot_Knocks ~ Site, AC.DF1, mean)
knock.se <- aggregate(Tot_Knocks ~ Site, AC.DF1, function(x) sd(x)/sqrt(length(x)))
knock.av$SE <- knock.se$Tot_Knocks
knock.av$U.SE <- knock.av$Tot_Knocks + knock.av$SE
knock.av$L.SE <- knock.av$Tot_Knocks - knock.av$SE

#making site a character
knock.av$Site <- as.character(knock.av$Site)

knock.CI <- ggplot(knock.av, aes(Site, Tot_Knocks)) + 
  geom_errorbar(aes(ymin = L.SE, ymax = U.SE), color = "black", width = 0) +
  geom_point(aes(fill = Site), color = "black", pch = 21, size = 6) +
  labs(x = "Site", y = "Tot_Knocks", title = "Total Knocks")
knock.CI



##Snaps

#snaps by site
snap.av <- aggregate(Snaps ~ Site, AC.DF1, mean)
snap.se <- aggregate(Snaps ~ Site, AC.DF1, function(x) sd(x)/sqrt(length(x)))
snap.av$SE <- snap.se$Snaps
snap.av$U.SE <- snap.av$Snaps + snap.av$SE
snap.av$L.SE <- snap.av$Snaps - snap.av$SE

#making site a character
snap.av$Site <- as.character(snap.av$Site)

snap.CI <- ggplot(snap.av, aes(Site, Snaps)) + 
  geom_errorbar(aes(ymin = L.SE, ymax = U.SE), color = "black", width = 0) +
  geom_point(aes(fill = Site), color = "black", pch = 21, size = 6) +
  labs(x = "Site", y = "Snaps", title = "Snaps per site")
snap.CI


##Long Calls

#LC by site
LC.av <- aggregate(Num_L_calls ~ Site, AC.DF1, mean)
LC.se <- aggregate(Num_L_calls ~ Site, AC.DF1, function(x) sd(x)/sqrt(length(x)))
LC.av$SE <- LC.se$Num_L_calls
LC.av$U.SE <- LC.av$Num_L_calls + LC.av$SE
LC.av$L.SE <- LC.av$Num_L_calls - LC.av$SE

#making site a character
LC.av$Site <- as.character(LC.av$Site)

LC.CI <- ggplot(LC.av, aes(Site, Num_L_calls)) + 
  geom_errorbar(aes(ymin = L.SE, ymax = U.SE), color = "black", width = 0) +
  geom_point(aes(fill = Site), color = "black", pch = 21, size = 6) +
  labs(x = "Site", y = "Long Calls", title = "Long Calls per site")
LC.CI

##Herbivory

#LC by site
H.av <- aggregate(Num_Herbivory ~ Site, AC.DF1, mean)
H.se <- aggregate(Num_Herbivory ~ Site, AC.DF1, function(x) sd(x)/sqrt(length(x)))
H.av$SE <- H.se$Num_Herbivory
H.av$U.SE <- H.av$Num_Herbivory + H.av$SE
H.av$L.SE <- H.av$Num_Herbivory - H.av$SE

#making site a character
H.av$Site <- as.character(H.av$Site)

H.CI <- ggplot(H.av, aes(Site, Num_Herbivory)) + 
  geom_errorbar(aes(ymin = L.SE, ymax = U.SE), color = "black", width = 0) +
  geom_point(aes(fill = Site), color = "black", pch = 21, size = 6) +
  labs(x = "Site", y = "Herbivory", title = "Herbivory per site")
H.CI




```
##Distributions

```{r histogram, echo = FALSE}
#plotting count histogram

Count.hist <- ggplot(data = AC.DF1, aes(AC.DF1$Tot_Knocks)) + geom_histogram()
Herb.hist <- ggplot(data = AC.DF1, aes(AC.DF1$Num_Herbivory)) + geom_histogram()
LC.hist <- ggplot(data = AC.DF1, aes(AC.DF1$Num_L_calls)) + geom_histogram()
Snap.hist <- ggplot(data = Snap.HF17, aes(Snap.HF17$Snaps)) + geom_histogram()

hist.p <- plot_grid(Count.hist, Herb.hist, LC.hist,Snap.hist, nrow = 2, ncol = 2)
hist.p

#plotting distributions of SPL response variables
MF.hist <- ggplot(data = AC.DF1, aes(AC.DF1$SPL_Midrange)) + geom_histogram() + ggtitle("MF SPL distribution")
#BB.hist <- ggplot(data = AC.DF1, aes(AC.DF1$SPL_BB)) + geom_histogram() + ggtitle("BB distribution")
HF.hist <- ggplot(data = AC.DF1, aes(AC.DF1$SPL_HF)) + geom_histogram() + ggtitle("HF SPL distribution")

hist1.p <- plot_grid(MF.hist, HF.hist, nrow = 1, ncol = 2)
hist1.p

#plotting distributions of ACI response variables
MF.hist1 <- ggplot(data = AC.DF1, aes(AC.DF1$ACI_Midrange)) + geom_histogram() + ggtitle("MF ACI distribution")
#BB.hist1 <- ggplot(data = AC.DF1, aes(AC.DF1$ACI_BB)) + geom_histogram()
HF.hist1 <- ggplot(data = AC.DF1, aes(AC.DF1$ACI_HF)) + geom_histogram() + ggtitle("HF ACI distribution")

hist2.p <- plot_grid(MF.hist1, HF.hist1, nrow = 1, ncol = 2)
hist2.p


```


##Scatterplots
###Scatterplots SPL
Plotting explanatory (Knocks, Calls, Herbivory, Snaps) against response variables (MF and HF) SPL
```{r scatterplots SPL, echo = FALSE}

#making site a character
AC.DF1$Site <- as.character(AC.DF1$Site)

#plotting total knocks against midrange SPL
SP.mf1 <- ggplot(AC.DF1, aes(Tot_Knocks, SPL_Midrange)) + geom_point() + ggtitle("Total Knocks effect on SPL MF")
SP.mf1.1 <- ggplot(AC.DF1, aes(Tot_Knocks, SPL_Midrange)) + geom_point(aes(color = Site)) + ggtitle("Total Knocks effect on SPL MF, split by site")
SP.mf1.2 <- ggplot(AC.DF1, aes(Tot_Knocks, SPL_Midrange)) + geom_point(aes(color = Hour)) + ggtitle("Total Knocks effect on SPL MF, split by hour")


SP.mf2 <- ggplot(AC.DF1, aes(Num_L_calls, SPL_Midrange)) + geom_point() + ggtitle("Long Calls effect on SPL MF")
SP.mf2.1 <- ggplot(AC.DF1, aes(Num_L_calls, SPL_Midrange)) + geom_point(aes(color = Site)) + ggtitle("Long Calls effect on SPL MF, split by site")
SP.mf2.2 <- ggplot(AC.DF1, aes(Num_L_calls, SPL_Midrange)) + geom_point(aes(color = Hour)) + ggtitle("Long Calls effect on SPL MF, split by hour")

SP.mf3 <- ggplot(AC.DF1, aes(Num_Herbivory, SPL_Midrange)) + geom_point() + ggtitle("Herbivory Sounds effect on SPL MF")

#checking for colinearity
SP.mfc1 <- ggplot(AC.DF1, aes(Tot_Knocks, Num_L_calls)) + geom_point() + ggtitle("Collinearity between Knocks and Long Calls")

SP.mfc2 <- ggplot(AC.DF1, aes(Tot_Knocks, Num_Herbivory)) + geom_point() + ggtitle("Collinearity between Knocks and Herbivory")

SP.mfc3 <- ggplot(AC.DF1, aes(Num_L_calls, Num_Herbivory)) + geom_point() + ggtitle("Collinearity between Herbivory and Long Calls")


#making site a character
Snap.HF17$Site.x<- as.character(Snap.HF17$Site.x)
Snap.HF18$Site.x<- as.character(Snap.HF18$Site.x)
Snap.HF$Site<- as.character(Snap.HF$Site)


SP.hf1 <- ggplot(Snap.HF17, aes(Snaps, SPL_HF)) + geom_point() + ggtitle("Snaps effect on SPL HF, 2017")
SP.hf2 <- ggplot(Snap.HF17, aes(Snaps, SPL_HF)) + geom_point(aes(color=Site.x)) + ggtitle("Snaps effect on SPL HF, 2017, split by site")

SP.hf3 <- ggplot(Snap.HF18, aes(Snaps, SPL_HF)) + geom_point() + ggtitle("Snaps effect on SPL HF, 2018")
SP.hf4 <- ggplot(Snap.HF18, aes(Snaps, SPL_HF)) + geom_point(aes(color=Site.x)) + ggtitle("Snaps effect on SPL HF, 2018, split by site")

#extreme outliers in 2018 - snap counts in the hundreds rather than thousands, going to find and remove them and run again
## Check that 2 divers were at all sites
low.snap <- Snap.HF18[Snap.HF18$Snaps <1000, ]
# Remove anything with fewer than 2 observers 

Snap.HF18E <- Snap.HF18[!(Snap.HF18$ds.id %in% low.snap$ds.id),]
#now rerunning without the 3 outliers

SP.hf3E <- ggplot(Snap.HF18E, aes(Snaps, SPL_HF)) + geom_point() + ggtitle("Snaps effect on SPL HF, 2018, outliers removed")
SP.hf4E <- ggplot(Snap.HF18E, aes(Snaps, SPL_HF)) + geom_point(aes(color=Site.x)) + ggtitle("Snaps effect on SPL HF, 2018, split by site, outliers removed")



#summing long calls and knocks
AC.DF1$Fish_Sounds <- AC.DF1$Tot_Knocks + AC.DF1$Num_L_calls

SP.mf4 <- ggplot(AC.DF1, aes(Fish_Sounds, SPL_Midrange)) + geom_point() + ggtitle("Combined Knocks and Calls vs. SPL MF")


SP.mf1
SP.mf1.1
SP.mf1.2

SP.mf2
SP.mf2.1
SP.mf2.2

SP.mf3
SP.mf4

SP.mfc1
SP.mfc2
SP.mfc3


SP.hf1
SP.hf2
SP.hf3
SP.hf4

SP.hf3E
SP.hf4E
```

###Scatterplots ACI
Plotting explanatory (Knocks, Calls, Herbivory, Snaps) against response variables (MF and HF) ACI
```{r scatterplots ACI, echo = FALSE}

#plotting ACI against explanatory factors
SP.acimf1 <- ggplot(AC.DF1, aes(Tot_Knocks, ACI_Midrange)) + geom_point() + ggtitle("Total Knocks effect on ACI MF")
SP.acimf1.1 <- ggplot(AC.DF1, aes(Tot_Knocks, ACI_Midrange)) + geom_point(aes(color = Site)) + ggtitle("Total Knocks effect on ACI MF, split by site")
SP.acimf1.2 <- ggplot(AC.DF1, aes(Tot_Knocks, ACI_Midrange)) + geom_point(aes(color = Hour)) + ggtitle("Total Knocks effect on ACI MF, split by hour")
SP.acimf2 <- ggplot(AC.DF1, aes(Num_L_calls, ACI_Midrange)) + geom_point() + ggtitle("Long Calls effect on ACI MF")
SP.acimf3 <- ggplot(AC.DF1, aes(Num_Herbivory, ACI_Midrange)) + geom_point() + ggtitle("Herbivory effect on ACI MF")

SP.acihf1 <- ggplot(AC.DF1, aes(Snaps, ACI_HF)) + geom_point() + ggtitle("Snaps effect on ACI HF")



SP.acimf1
SP.acimf1.1
SP.acimf1.2
SP.acimf2
SP.acimf3

SP.acihf1

```



##Patterns Breakdown SPL and ACI
###Patterns in Tot_Knocks and Hour at Site and Hour Level - SPL
Breaking down the relationship between total knocks and MF to the site and hour level
```{r MF & Knocks Breakdown, echo = FALSE}
#splitting dataframe by site
s5 <- filter(AC.DF1, Site == "5")
s32 <- filter(AC.DF1, Site == "32")
s35 <- filter(AC.DF1, Site == "35")
s40 <- filter(AC.DF1, Site == "40")
s8 <- filter(AC.DF1, Site == "8")

#splitting dataframe by hour
h3 <- filter(AC.DF1, Hour == "3")
h9 <- filter(AC.DF1, Hour == "9")
h15 <- filter(AC.DF1, Hour == "15")
h21 <- filter(AC.DF1, Hour == "21")

#plotting scatterplots by site
SPmf.5 <- ggplot(s5, aes(Tot_Knocks, SPL_Midrange)) + geom_point(color = "Green") +ggtitle("Site 5")

SPmf.32 <- ggplot(s32, aes(Tot_Knocks, SPL_Midrange)) + geom_point(color = "Red") + ggtitle("Site 32")

SPmf.35 <- ggplot(s35, aes(Tot_Knocks, SPL_Midrange)) + geom_point(color = "Orange") + ggtitle("Site 35")

SPmf.40 <- ggplot(s40, aes(Tot_Knocks, SPL_Midrange)) + geom_point(color = "Red") + ggtitle("Site 40")

SPmf.8 <- ggplot(s8, aes(Tot_Knocks, SPL_Midrange)) + geom_point(color = "Orange") + ggtitle("Site 8")


SPmf.5
SPmf.35
SPmf.8
SPmf.40
SPmf.32
#plotting scatterplots by hour
SPmf.h3 <- ggplot(h3, aes(Tot_Knocks, SPL_Midrange)) + geom_point() + ggtitle("3 AM")
SPmf.h3

SPmf.h9 <- ggplot(h9, aes(Tot_Knocks, SPL_Midrange)) + geom_point() + ggtitle("9 AM")
SPmf.h9

SPmf.h15 <- ggplot(h15, aes(Tot_Knocks, SPL_Midrange)) + geom_point() + ggtitle("3 PM")
SPmf.h15

SPmf.h21 <- ggplot(h21, aes(Tot_Knocks, SPL_Midrange)) + geom_point() + ggtitle("9 PM")
SPmf.h21

```

###Patterns in HF and Snaps at Site Level - SPL
```{r patternsHF&Snaps, echo = FALSE}
SP.t1 <- ggplot(Snap.HF, aes(Time, Snaps)) + geom_point(aes(color = Site))
SP.t1
#splitting snaps by site
#splitting dataframe by site
s5 <- filter(Snap.HF, Site == "5")
s32 <- filter(Snap.HF, Site == "32")
s35 <- filter(Snap.HF, Site == "35")
s40 <- filter(Snap.HF, Site == "40")
s8 <- filter(Snap.HF, Site == "8")

#plotting by site
SP.t5 <- ggplot(s5, aes(Time, Snaps)) + geom_point(color = "Green") + ggtitle("Site 5")

SP.t32 <- ggplot(s32, aes(Time, Snaps)) + geom_point(color = "Red" ) + ggtitle("Site 32")

SP.t35 <- ggplot(s35, aes(Time, Snaps)) + geom_point(color = "Orange") + ggtitle("Site 35")

SP.t40 <- ggplot(s40, aes(Time, Snaps)) + geom_point(color = "Red") + ggtitle("Site 40")

SP.t8 <- ggplot(s8, aes(Time, Snaps)) + geom_point(color = "Orange") + ggtitle("Site 8")

SP.t5
SP.t8
SP.t35
SP.t40
SP.t32


##regressions by site
SPhf.5 <- ggplot(s5, aes(Snaps, SPL_HF)) + geom_point(color = "Green") + ggtitle("Site 5")

SPhf.32 <- ggplot(s32, aes(Snaps, SPL_HF)) + geom_point(color = "Red") + ggtitle("Site 32")

SPhf.35 <- ggplot(s35, aes(Snaps, SPL_HF)) + geom_point(color = "Orange") + ggtitle("Site 35")

SPhf.40 <- ggplot(s40, aes(Snaps, SPL_HF)) + geom_point(color = "Red") + ggtitle("Site 40")

SPhf.8 <- ggplot(s8, aes(Snaps, SPL_HF)) + geom_point(color = "Orange") + ggtitle("Site 8")

SPhf.5
SPhf.8
SPhf.35
SPhf.40
SPhf.32


```

###Patterns in Tot_Knocks and Hour at Site and Hour Level - ACI
```{r MF & Knocks Breakdown - ACI, echo = FALSE}
#splitting dataframe by site
s5 <- filter(AC.DF1, Site == "5")
s32 <- filter(AC.DF1, Site == "32")
s35 <- filter(AC.DF1, Site == "35")
s40 <- filter(AC.DF1, Site == "40")
s8 <- filter(AC.DF1, Site == "8")

#splitting dataframe by hour
h3 <- filter(AC.DF1, Hour == "3")
h9 <- filter(AC.DF1, Hour == "9")
h15 <- filter(AC.DF1, Hour == "15")
h21 <- filter(AC.DF1, Hour == "21")

#plotting scatterplots by site
SPmf.aci.5 <- ggplot(s5, aes(Tot_Knocks, ACI_Midrange)) + geom_point(color = "Green") +ggtitle("Site 5")

SPmf.aci.32 <- ggplot(s32, aes(Tot_Knocks, ACI_Midrange)) + geom_point(color = "Red") + ggtitle("Site 32")

SPmf.aci.35 <- ggplot(s35, aes(Tot_Knocks, ACI_Midrange)) + geom_point(color = "Orange") + ggtitle("Site 35")

SPmf.aci.40 <- ggplot(s40, aes(Tot_Knocks, ACI_Midrange)) + geom_point(color = "Red") + ggtitle("Site 40")

SPmf.aci.8 <- ggplot(s8, aes(Tot_Knocks, ACI_Midrange)) + geom_point(color = "Orange") + ggtitle("Site 8")


SPmf.aci.5
SPmf.aci.35
SPmf.aci.8
SPmf.aci.40
SPmf.aci.32
#plotting scatterplots by hour
SPmf.aci.h3 <- ggplot(h3, aes(Tot_Knocks, ACI_Midrange)) + geom_point() + ggtitle("3 AM")
SPmf.aci.h3

SPmf.aci.h9 <- ggplot(h9, aes(Tot_Knocks, ACI_Midrange)) + geom_point() + ggtitle("9 AM")
SPmf.aci.h9

SPmf.aci.h15 <- ggplot(h15, aes(Tot_Knocks, ACI_Midrange)) + geom_point() + ggtitle("3 PM")
SPmf.aci.h15

SPmf.aci.h21 <- ggplot(h21, aes(Tot_Knocks, ACI_Midrange)) + geom_point() + ggtitle("9 PM")
SPmf.aci.h21

```


##Regressions
###Regressions - SPL
Running basic regressions linking the explanatory to the response at their lowest levels and combined to see how different sites/ hours change the regression - SPL
```{r regressions, echo = FALSE}
#equation for r^2 value

SP.mf1.1 + ggtitle("Total Knocks effect on SPL MF, split by site") + stat_smooth(method = "glm") 
kmf.lm = lm(SPL_Midrange ~ Tot_Knocks, data = AC.DF1)
summary(kmf.lm)$r.squared

SP.mf1.2 + ggtitle("Total Knocks effect on SPL MF, split by hour") + geom_smooth(method = "glm")
kmf.lm = lm(SPL_Midrange ~ Tot_Knocks, data = AC.DF1)
summary(kmf.lm)$r.squared

SP.hf2 + geom_smooth(method = "glm") + ggtitle("Total Snaps and SPL HF, 2017")
shf.lm17 = lm(SPL_HF ~ Snaps, data = Snap.HF17)
summary(shf.lm17)$r.squared


SP.hf4E + geom_smooth(method = "glm") + ggtitle("Total Snaps and SPL HF, 2018")
shf.lm18 = lm(SPL_HF ~ Snaps, data = Snap.HF18)
summary(shf.lm18)$r.squared

SPmf.5 + geom_smooth(method = "glm") + ggtitle("Site 5, MF SPL")
s5mf.lm = lm(SPL_Midrange ~ Tot_Knocks, data = s5)
summary(s5mf.lm)$r.squared

SPmf.35 + geom_smooth(method = "glm") + ggtitle("Site 35, MF SPL")
s35mf.lm = lm(SPL_Midrange ~ Tot_Knocks, data = s35)
summary(s35mf.lm)$r.squared

SPmf.8 + geom_smooth(method = "glm") + ggtitle("Site 8, MF SPL")
s8mf.lm = lm(SPL_Midrange ~ Tot_Knocks, data = s8)
summary(s8mf.lm)$r.squared

SPmf.40 + geom_smooth(method = "glm") + ggtitle("Site 40, MF SPL")
s40mf.lm = lm(SPL_Midrange ~ Tot_Knocks, data = s40)
summary(s40mf.lm)$r.squared

SPmf.32 + geom_smooth(method = "glm") + ggtitle("Site 32, MF SPL")
s32mf.lm = lm(SPL_Midrange ~ Tot_Knocks, data = s32)
summary(s32mf.lm)$r.squared

SPmf.h3 + geom_smooth(method = "glm") + ggtitle("3 AM, MF SPL")
h3mf.lm = lm(SPL_Midrange ~ Tot_Knocks, data = h3)
summary(h3mf.lm)$r.squared

SPmf.h9 + geom_smooth(method = "glm") + ggtitle("9 AM, MF SPL")
h9mf.lm = lm(SPL_Midrange ~ Tot_Knocks, data = h9)
summary(h9mf.lm)$r.squared

SPmf.h15 + geom_smooth(method = "glm") + ggtitle("3 PM, MF SPL")
h15mf.lm = lm(SPL_Midrange ~ Tot_Knocks, data = h15)
summary(h15mf.lm)$r.squared

SPmf.h21 + geom_smooth(method = "glm") + ggtitle("9 PM, MF SPL")
h21mf.lm = lm(SPL_Midrange ~ Tot_Knocks, data = h21)
summary(h21mf.lm)$r.squared

```

###Regressions - ACI
Running basic regressions linking the explanatory to the response at their lowest levels and combined to see how different sites/ hours change the regression - ACI
```{r regressions ACI, echo = FALSE}
SPmf.aci.5 + geom_smooth(method = "glm") + ggtitle("Site 5, MF ACI")
s5amf.lm = lm(ACI_Midrange ~ Tot_Knocks, data = s5)
summary(s5amf.lm)$r.squared

SPmf.aci.35 + geom_smooth(method = "glm") + ggtitle("Site 35, MF ACI")
s35amf.lm = lm(ACI_Midrange ~ Tot_Knocks, data = s35)
summary(s35amf.lm)$r.squared

SPmf.aci.8 + geom_smooth(method = "glm") + ggtitle("Site 8, MF ACI")
s8amf.lm = lm(ACI_Midrange ~ Tot_Knocks, data = s8)
summary(s8amf.lm)$r.squared

SPmf.aci.40 + geom_smooth(method = "glm") + ggtitle("Site 40, MF ACI")
s40amf.lm = lm(ACI_Midrange ~ Tot_Knocks, data = s40)
summary(s40amf.lm)$r.squared

SPmf.aci.32 + geom_smooth(method = "glm") + ggtitle("Site 32, MF ACI")
s32amf.lm = lm(ACI_Midrange ~ Tot_Knocks, data = s32)
summary(s32amf.lm)$r.squared

SPmf.aci.h3 + geom_smooth(method = "glm") + ggtitle("3 AM, MF ACI")
h3amf.lm = lm(ACI_Midrange ~ Tot_Knocks, data = h3)
summary(h3amf.lm)$r.squared

SPmf.aci.h9 + geom_smooth(method = "glm") + ggtitle("9 AM, MF ACI")
h9amf.lm = lm(ACI_Midrange ~ Tot_Knocks, data = h9)
summary(h9amf.lm)$r.squared

SPmf.aci.h15 + geom_smooth(method = "glm") + ggtitle("3 PM, MF ACI")
h15amf.lm = lm(ACI_Midrange ~ Tot_Knocks, data = h15)
summary(h15amf.lm)$r.squared

SPmf.aci.h21 + geom_smooth(method = "glm") + ggtitle("9 PM, MF ACI")
h21amf.lm = lm(ACI_Midrange ~ Tot_Knocks, data = h21)
summary(h21amf.lm)$r.squared
```