---
title: "Results_NEW_ALL"
author: "Sean Dimoff"
date: 27/05/20
output: 
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
---

```{r setup, include=FALSE}
library(ggplot2)
library(cowplot)
library(rmarkdown)
library(knitr)
library(RColorBrewer)
library(GGally)
library(mctest)
library(usdm)
library(hms)
library(dplyr)
library(lme4)
library(MASS)
library(lmerTest)
library(goft)
library(magick)
library(MuMIn)
library(car)
library(gridExtra)
library(patchwork)
library(arm)
#library(sjPlot)
#library(sjlabelled)
#library(sjmisc)


#loading in SPL data

load("../Raw_Data/SPLHF17long.Rdata")
load("../Raw_Data/SPLHF18long.Rdata")


load("../Raw_Data/SPLMF17long.Rdata")
load("../Raw_Data/SPLMF18long.Rdata")


load("../Raw_Data/SPLHFlong.Rdata")
load("../Raw_Data/SPLMFlong.Rdata")

load("../Raw_Data/SPLMF.long.wind.Rdata")

#combined SPL and HF dataframes
load("../Raw_Data/Snap.HF17.Rdata")
load("../Raw_Data/Snap.HF18.Rdata")
#changing site to a character
Snap.HF17$Site.x <- as.character(Snap.HF17$Site.x)
Snap.HF18$Site.x <- as.character(Snap.HF18$Site.x)

load("../Raw_Data/Snap.HF.Rdata")

##loading in the full dataframe with all data
#load("../Raw_Data/AC.DF.Rdata")
load("../Raw_Data/AC.DF1.Rdata")

#loading in boat.list
load("../Raw_Data/boatlist.Rdata")

#loading in MF ACI data for diurnal plot
load("../Raw_Data/ACI_MF_tot.Rdata")

#loading in Selection tables
sel.tbl <- read.csv("../Raw_Data/Knock_Selections.csv")

#removing site/date id's from AC.DF1 that have boat noise in the files
AC.DF1 <- AC.DF1[!(AC.DF1$st.id %in% boat.list),]

#removes 4 from 40, 2 from 32, 1 from 35, and one from 5

#making site a character
AC.DF1$Site <- as.character(AC.DF1$Site)

#making duplicate dataframes
AC.DF1C <- AC.DF1

Snap.HF17C <- Snap.HF17
Snap.HF18C <- Snap.HF18

#Creating centered AC.DF1 dataframe
AC.DF1C$Snaps <- rescale(AC.DF1C$Snaps, "center")
AC.DF1C$Tot_Knocks <- rescale(AC.DF1C$Tot_Knocks, "center")
AC.DF1C$Num_Herbivory <- rescale(AC.DF1C$Num_Herbivory, "center")
AC.DF1C$Num_L_calls <- rescale(AC.DF1C$Num_L_calls, "center")

#creating centered Snap.HF17 and 18 dataframes
Snap.HF17C$SPL_HF <- rescale(Snap.HF17C$SPL_HF, "center")
Snap.HF18C$SPL_HF <- rescale(Snap.HF18C$SPL_HF, "center")


#removing outliers from Snap.HF dataframe
low.snap <- Snap.HF[Snap.HF$Snaps <1000, ]
# Remove anything with fewer than 2 observers 
Snap.HF <- Snap.HF[!(Snap.HF$ds.id %in% low.snap$ds.id),]

#making a snap.hf dataframe to center
Snap.HFC <- Snap.HF

Snap.HFC$Snaps <- rescale(Snap.HFC$Snaps, "center")

#subsetting only lm variables
AC.DF1Co <- subset(AC.DF1C, select = c(SPL_Midrange, ACI_Midrange, Tot_Knocks, Num_L_calls, Num_Herbivory, Site, Hour, Year, Date))

#making Hour ordinal
#AC.DF1Co$Hour_factor <- factor (AC.DF1$Hour, order = TRUE, levels = c("3", "9", "15", "21"))


#splitting dataframe by site
s5 <- filter(AC.DF1, Site == "5")
s32 <- filter(AC.DF1, Site == "32")
s35 <- filter(AC.DF1, Site == "35")
s40 <- filter(AC.DF1, Site == "40")
s8 <- filter(AC.DF1, Site == "8")

#splitting dataframe by hour
h3 <- filter(AC.DF1, Hour == "3")
h9 <- filter(AC.DF1, Hour == "9")
h15 <- filter(AC.DF1, Hour == "15")
h21 <- filter(AC.DF1, Hour == "21")

#creating new variable for site_year
Snap.HF$site_year <- paste(Snap.HF$Site, Snap.HF$Year, sep= "_")
AC.DF1Co$site_year <- paste(AC.DF1Co$Site, AC.DF1Co$Year, sep= "_")


#Adding in continuous fishing pressure variable to dataframes used for modelling
sites <- read.csv("../Raw_Data/KI_Sites_Sept2019.csv", header = TRUE, stringsAsFactors = FALSE)
#renaming the first column so that it doesn't have unknown characters
colnames(sites)[1] <- "site"

Snap.HF$fp.cont <-  sites$continous.pressure.2km[match(Snap.HF$Site, sites$site)]
AC.DF1Co$fp.cont <- sites$continous.pressure.2km[match(AC.DF1Co$Site, sites$site)]

#centering fp.cont
Snap.HF$fp.cont <- rescale(Snap.HF$fp.cont, "center")
AC.DF1Co$fp.cont <- rescale(AC.DF1Co$fp.cont, "center")

##loading in lunar phase data
#load("../Raw_Data/LunarPhase2017.Rdata")
#load("../Raw_Data/LunarPhase2018.Rdata")
load("../Raw_Data/LunarPhase2017_format.Rdata")
load("../Raw_Data/LunarPhase2018_format.Rdata")
#save(lp2018a, file = "../Raw_Data/LunarPhase2018_format")

#combining these dataframes
#Lunar.phase.snap <- rbind(lp2017, lp2018)
Lunar.phase.fish <- rbind(lp2017a, lp2018a)
#matching lunar phase  #never this easy - the dates don't match up, need to investigate
Snap.HF$lunar.phase.sine <- Lunar.phase.fish$lunar.sine.x[match(Snap.HF$Date, Lunar.phase.fish$Date.b)]
Snap.HF$lunar.phase.cos <- Lunar.phase.fish$lunar.cos.x[match(Snap.HF$Date, Lunar.phase.fish$Date.b)]

AC.DF1Co$lunar.phase.sine <- Lunar.phase.fish$lunar.sine.x[match(AC.DF1Co$Date, Lunar.phase.fish$Date.a)]
AC.DF1Co$lunar.phase.cos <- Lunar.phase.fish$lunar.cos.x[match(AC.DF1Co$Date, Lunar.phase.fish$Date.a)]

sum(is.na(Snap.HF$lunar.phase.sine))
sum(is.na(Snap.HF$lunar.phase.cos))
sum(is.na(AC.DF1Co$lunar.phase.sine))
sum(is.na(AC.DF1Co$lunar.phase.cos))
#need to add date to the AC.DF1Co 

```

**Exploratory Plots for 2017-2018 Acoustic/Fish Data**

**Purpose** To run and select my new final models for the acoustic manuscript

I have summarized results at the top here, but please scroll down if you would like to see the outputs of the linear models and further analysis into each of the selected models, how they compare with my results when I included random effects, and comparisons between "matching" models if the new selected models aren't the same as those selected when random effects were included.

*Note* 

Any models that use MF - are actually my low frequency models - this is just an artifact from the beginning of the project.

fishing pressure has now been centered.

In the low frequencies, Lunar phase category "First Quarter" cannot be analyzed because it is the only category of lunar phase in 2018 and therefore they are collinear.

#Results Summarized

Sine was chosen over cosine as it was fit the high frequency SPL better than cosine, although neither were significant for all other response variables.

**SPL HF**



**SPL LF**



**ACI HF **



**ACI LF**


#Sine vs Cos Models
## SPL HF Model


```{r simple model sin vs. cos, echo = TRUE}
Snap.HF$Year <- as.character(Snap.HF$Year)
simple.model.sin <- lm(SPL_HF ~ Snaps + Year + lunar.phase.sine, data = Snap.HF)
simple.model.cos <- lm(SPL_HF ~ Snaps + Year + lunar.phase.cos, data = Snap.HF)

```

```{r simple model2 sin vs. cos, echo= TRUE}
simple.model1.sin <- lm(SPL_HF ~ Snaps + dn + Year + lunar.phase.sine, data = Snap.HF)
simple.model1.cos <- lm(SPL_HF ~ Snaps + dn + Year + lunar.phase.cos, data = Snap.HF)

```

```{r simple model3 sin vs. cos, echo = TRUE}

simple.model3.sin <- lm(SPL_HF ~ Snaps*dn + Year + lunar.phase.sine, data = Snap.HF)
simple.model3.cos <- lm(SPL_HF ~ Snaps*dn + Year + lunar.phase.cos, data = Snap.HF)

```

###Model Selection

```{r hf sin vs cos spl selection, echo = TRUE}

#coming up with several variations on the models presented above

#testing each of the models

splhftbl <- AICc(simple.model.sin, simple.model.cos, simple.model1.sin, simple.model1.cos, simple.model3.sin, simple.model3.cos)

splhftbl$minAIC <- 78411.93
splhftbl$deltaAIC <- splhftbl$AICc - splhftbl$minAIC

splhftbl
summary(simple.model3.sin)

```

**Same model is picked as when random effects are included**



## ACI HF Model

```{r hf sine vs cos aci step, echo = TRUE}
aci.hf.sine <- lm(ACI_HF ~ Snaps *dn + Year + lunar.phase.sine, data = Snap.HF)
aci.hf.cos <- lm(ACI_HF ~ Snaps * dn + Year + lunar.phase.cos, data = Snap.HF)

summary(aci.hf.sine)
summary(aci.hf.cos)
```

sine and cosine do not make a difference in ACI and are not significant, regardless of the formula used to test them.


## LF SPL Model


```{r sine vs cos 1 mf model, echo = TRUE}

simple1mf.sine <- lm(SPL_Midrange ~ Tot_Knocks + Year + lunar.phase.sine, data = AC.DF1Co)
simple1mf.cos <- lm(SPL_Midrange ~ Tot_Knocks + Year + lunar.phase.cos, data = AC.DF1Co)


```


```{r sine vs cos 2 mf model, echo = TRUE}

simple2mf.sine <- lm(SPL_Midrange ~ Tot_Knocks + Num_Herbivory + Num_L_calls + Hour + Year + lunar.phase.sine, data = AC.DF1Co)
simple2mf.cos <- lm(SPL_Midrange ~ Tot_Knocks + Num_Herbivory + Num_L_calls + Hour + Year + lunar.phase.cos, data = AC.DF1Co)


```



```{r simple4 mf model, echo = TRUE}

simple4mf.sine <- lm(SPL_Midrange ~ Tot_Knocks + Num_Herbivory + Num_L_calls + Hour + Tot_Knocks:Hour + Year + lunar.phase.sine, data = AC.DF1Co)
simple4mf.cos <- lm(SPL_Midrange ~ Tot_Knocks + Num_Herbivory + Num_L_calls + Hour + Tot_Knocks:Hour + Year + lunar.phase.cos, data = AC.DF1Co)
#All call types affect MF SPL, however, only knocks changes its effect size throughout the day

```


```{r simple7 mf model, echo = TRUE}

simple7mf.sine <- lm(SPL_Midrange ~ Tot_Knocks + Num_Herbivory + Num_L_calls + Hour + Year + Tot_Knocks:Hour + Num_Herbivory:Hour + Num_L_calls:Hour + lunar.phase.sine, data = AC.DF1Co)

simple7mf.cos <- lm(SPL_Midrange ~ Tot_Knocks + Num_Herbivory + Num_L_calls + Hour + Year + Tot_Knocks:Hour + Num_Herbivory:Hour + Num_L_calls:Hour + lunar.phase.cos, data = AC.DF1Co)


```

```{r simple reduced mf models, echo = FALSE}

reducemf4sine <- lm(SPL_Midrange ~ Tot_Knocks + Hour + Tot_Knocks:Hour + Year + lunar.phase.sine, data = AC.DF1Co)
reducemf4cos <- lm(SPL_Midrange ~ Tot_Knocks + Hour + Tot_Knocks:Hour + Year + lunar.phase.cos, data = AC.DF1Co)
#The effect of knocks on MF SPL changes throughout the day

#reducemf5 <- lmer(SPL_Midrange ~ Tot_Knocks + Hour + Tot_Knocks:Hour + Num_L_calls + (1|Site)+(1|Year), data = AC.DF1Co)
#model fails to converge

reducemf6sine <- lm(SPL_Midrange ~ Tot_Knocks + Hour + Tot_Knocks:Hour + Num_Herbivory + Year + lunar.phase.sine, data = AC.DF1Co)
reducemf6cos <- lm(SPL_Midrange ~ Tot_Knocks + Hour + Tot_Knocks:Hour + Num_Herbivory + Year + lunar.phase.cos, data = AC.DF1Co)

#the effect of knocks on MF SPL changes throughout the day and herbivory is also loud enough to affect MF SPL

reducemf7sine <- lm(SPL_Midrange ~Tot_Knocks*lunar.phase.sine + Hour + Tot_Knocks + Num_Herbivory + Year, data = AC.DF1Co)
reducemf7cos <- lm(SPL_Midrange ~Tot_Knocks*lunar.phase.cos + Hour + Tot_Knocks + Num_Herbivory + Year, data = AC.DF1Co)

```



###Model Selection


```{r model selection mf spl, echo = TRUE}

splmftbl <- AICc(simple1mf.sine, simple1mf.cos, simple2mf.sine, simple2mf.cos, simple4mf.sine, simple4mf.cos, simple7mf.sine, simple7mf.cos, reducemf4sine, reducemf4cos, reducemf7sine, reducemf7cos)

splmftbl$minAIC <- 881.9244
splmftbl$deltaAIC <- splmftbl$AICc - splmftbl$minAIC

splmftbl

splmftbl.short <- subset(splmftbl, deltaAIC < 6)

splmftbl.short

summary(simple4mf.sine)
summary(simple4mf.cos)

```

Neither sine or cosine is significant here.


## LF ACI Model

```{r mf aci1 sine vs cos, echo = FALSE}

mf.aci1sine <- lm(ACI_Midrange ~ Tot_Knocks + Num_Herbivory + Num_L_calls + Year + Hour + lunar.phase.sine, data = AC.DF1Co)
mf.aci1cos <- lm(ACI_Midrange ~ Tot_Knocks + Num_Herbivory + Num_L_calls + Year + Hour + lunar.phase.cos, data = AC.DF1Co)

summary(mf.aci1sine)
summary(mf.aci1cos)
```


```{r mf acimax sine vs cos, echo = FALSE}

#maximal model
mf.maxaci.sine <- lm(ACI_Midrange ~ (Tot_Knocks + Num_L_calls + Num_Herbivory)*Hour + Year + lunar.phase.sine, data = AC.DF1Co)
mf.maxaci.cos <- lm(ACI_Midrange ~ (Tot_Knocks + Num_L_calls + Num_Herbivory)*Hour + Year + lunar.phase.sine, data = AC.DF1Co)

summary(mf.maxaci.sine)
summary(mf.maxaci.cos)

```


```{r mf aci2 sine vs cos , echo = FALSE}

mf.aci2sine <- lm(ACI_Midrange ~ Tot_Knocks + Hour + Year + lunar.phase.sine, data = AC.DF1Co)
mf.aci2cos <- lm(ACI_Midrange ~ Tot_Knocks + Hour + Year + lunar.phase.cos, data = AC.DF1Co)

summary(mf.aci2sine)
summary(mf.aci2cos)
```


```{r mfaci3 sine vs cos, echo = FALSE}

mf.aci3sine <- lm(ACI_Midrange ~ Tot_Knocks*Hour + Year + lunar.phase.sine, data = AC.DF1Co)
mf.aci3cos <- lm(ACI_Midrange ~ Tot_Knocks*Hour + Year + lunar.phase.sine, data = AC.DF1Co)
#intercept model

#inter.mfaci <- lmer(ACI_Midrange ~ 1 + (1|site_year), data = AC.DF1Co)

```

###Model Selection

```{r mf aci sine vs cos model selection, echo = TRUE}

acimftbl <-AICc(mf.aci1sine, mf.aci1cos, mf.aci2sine, mf.aci2cos, mf.aci3sine, mf.aci3cos)

acimftbl$minAIC <- 4060.373
acimftbl$deltaAIC <- acimftbl$AICc - acimftbl$minAIC

acimftbl

acimftbl.short <- subset(acimftbl, deltaAIC < 6)

acimftbl.short

```

**The selected model is different from the selected model including random effects**

The model with the lowest AIC here is my simplest model including only knocks, fishing pressure, year, and lunar phase.  
```{r summary sine aci mf, echo = TRUE}
summary(mf.aci2sine)
summary(mf.aci2cos)
```

Now knocks are significant... I wonder if this comes from centering using arm rather than center_scale

However, this model still explains 1% of variation.

Neither sine or cosine are important here.




#Sine vs Year Models
## SPL HF Model


```{r simple model sin vs. year, echo = TRUE}
Snap.HF$Year <- as.character(Snap.HF$Year)

simple.model <- lm(SPL_HF ~ Snaps + Year + lunar.phase.sine + fp.cont, data = Snap.HF)

```

Interesting that the sine model here explains alot more than both the year and combo models??

```{r simple model2 sin vs. year, echo= TRUE}
simple.model1<- lm(SPL_HF ~ Snaps + dn + Year + lunar.phase.sine + fp.cont, data = Snap.HF)
```



```{r simple model3 sin vs. year, echo = TRUE}

simple.model3 <- lm(SPL_HF ~ Snaps*dn + lunar.phase.sine + Year + fp.cont, data = Snap.HF)

```

###Model Selection

```{r hf sin vs year spl selection, echo = TRUE}

#coming up with several variations on the models presented above

#testing each of the models

splhftbl <- AICc(simple.model, simple.model1, simple.model3)

splhftbl$minAIC <- 77923.39
splhftbl$deltaAIC <- splhftbl$AICc - splhftbl$minAIC

splhftbl
summary(simple.model3)

```




## ACI HF Model

```{r hf sine vs year aci step, echo = TRUE}
aci.hf <- lm(ACI_HF ~ Snaps*dn + Year + lunar.phase.sine + fp.cont, data = Snap.HF)
aci.hf1 <- lm(ACI_HF ~ Snaps + Year + lunar.phase.sine + fp.cont, data = Snap.HF)
aci.hf2 <- lm(ACI_HF ~ Snaps+ dn + Year + lunar.phase.sine + fp.cont, data = Snap.HF)


acihftbl <- AICc(aci.hf, aci.hf1, aci.hf2)
acihftbl$minAIC <- 319647.7
acihftbl$deltaAIC <- acihftbl$AICc - acihftbl$minAIC
acihftbl

summary(aci.hf1)

```

I am choosing the aci.hf1 model here which does not include day/night.  This is because it has the lowest df, but also is within delta AIC < 2.


## LF SPL Model


```{r sine vs year 1 mf model, echo = TRUE}

simple1mf.sine <- lm(SPL_Midrange ~ Tot_Knocks + lunar.phase.sine, data = AC.DF1Co)
simple1mf.year <- lm(SPL_Midrange ~ Tot_Knocks + Year, data = AC.DF1Co)
simple1mf.combo <- lm(SPL_Midrange ~ Tot_Knocks + lunar.phase.sine + Year, data = AC.DF1Co)


```


```{r sine vs year 2 mf model, echo = TRUE}

simple2mf.sine <- lm(SPL_Midrange ~ Tot_Knocks + Num_Herbivory + Num_L_calls + Hour + lunar.phase.sine, data = AC.DF1Co)
simple2mf.combo <- lm(SPL_Midrange ~ Tot_Knocks + Num_Herbivory + Num_L_calls + Hour + Year + lunar.phase.sine, data = AC.DF1Co)
simple2mf.year <- lm(SPL_Midrange ~ Tot_Knocks + Num_Herbivory + Num_L_calls + Hour + Year, data = AC.DF1Co)

```



```{r simple4 year mf model, echo = TRUE}

simple4mf.sine <- lm(SPL_Midrange ~ Tot_Knocks + Num_Herbivory + Num_L_calls + Hour + Tot_Knocks:Hour + lunar.phase.sine, data = AC.DF1Co)
simple4mf.combo <- lm(SPL_Midrange ~ Tot_Knocks + Num_Herbivory + Num_L_calls + Hour + Tot_Knocks:Hour + Year + lunar.phase.sine, data = AC.DF1Co)
simple4mf.year <- lm(SPL_Midrange ~ Tot_Knocks + Num_Herbivory + Num_L_calls + Hour + Tot_Knocks:Hour + Year, data = AC.DF1Co)
#All call types affect MF SPL, however, only knocks changes its effect size throughout the day

```


```{r simple7 year mf model, echo = TRUE}

simple7mf.sine <- lm(SPL_Midrange ~ Tot_Knocks + Num_Herbivory + Num_L_calls + Hour + Tot_Knocks:Hour + Num_Herbivory:Hour + Num_L_calls:Hour + lunar.phase.sine, data = AC.DF1Co)

simple7mf.combo <- lm(SPL_Midrange ~ Tot_Knocks + Num_Herbivory + Num_L_calls + Hour + Year + Tot_Knocks:Hour + Num_Herbivory:Hour + Num_L_calls:Hour + lunar.phase.sine, data = AC.DF1Co)

simple7mf.year <- lm(SPL_Midrange ~ Tot_Knocks + Num_Herbivory + Num_L_calls + Hour + Year + Tot_Knocks:Hour + Num_Herbivory:Hour + Num_L_calls:Hour, data = AC.DF1Co)

```

```{r simple year reduced mf models, echo = FALSE}

reducemf4sine <- lm(SPL_Midrange ~ Tot_Knocks + Hour + Tot_Knocks:Hour + lunar.phase.sine, data = AC.DF1Co)
reducemf4combo <- lm(SPL_Midrange ~ Tot_Knocks + Hour + Tot_Knocks:Hour + Year + lunar.phase.sine, data = AC.DF1Co)
reducemf4year <- lm(SPL_Midrange ~ Tot_Knocks + Hour + Tot_Knocks:Hour + Year, data = AC.DF1Co)
#The effect of knocks on MF SPL changes throughout the day

#reducemf5 <- lmer(SPL_Midrange ~ Tot_Knocks + Hour + Tot_Knocks:Hour + Num_L_calls + (1|Site)+(1|Year), data = AC.DF1Co)
#model fails to converge

reducemf6sine <- lm(SPL_Midrange ~ Tot_Knocks + Hour + Tot_Knocks:Hour + Num_Herbivory + lunar.phase.sine, data = AC.DF1Co)
reducemf6combo <- lm(SPL_Midrange ~ Tot_Knocks + Hour + Tot_Knocks:Hour + Num_Herbivory + Year + lunar.phase.sine, data = AC.DF1Co)
reducemf6year <- lm(SPL_Midrange ~ Tot_Knocks + Hour + Tot_Knocks:Hour + Num_Herbivory + Year, data = AC.DF1Co)

#the effect of knocks on MF SPL changes throughout the day and herbivory is also loud enough to affect MF SPL


```



###Model Selection


```{r model year selection mf spl, echo = TRUE}

splmftbl <- AICc(simple1mf.sine, simple1mf.combo, simple1mf.year, simple2mf.sine, simple2mf.combo, simple2mf.year, simple4mf.sine, simple4mf.combo, simple4mf.year, simple7mf.sine, simple7mf.combo, simple7mf.year, reducemf4sine, reducemf4combo, reducemf4year, reducemf6sine, reducemf6combo, reducemf6year)

  splmftbl$minAIC <- 879.4773
splmftbl$deltaAIC <- splmftbl$AICc - splmftbl$minAIC

splmftbl

splmftbl.short <- subset(splmftbl, deltaAIC < 6)

splmftbl.short

summary(reducemf6year)

```

Year is significant, sine in the same formula is not significant.  

I chose the most parsimonious model that had a delta ACI < 2.  The "best" model was maximal.


## LF ACI Model

```{r mf aci1 sine vs year, echo = FALSE}

mf.aci1sine <- lm(ACI_Midrange ~ Tot_Knocks + Num_Herbivory + Num_L_calls + Hour + lunar.phase.sine, data = AC.DF1Co)
mf.aci1combo <- lm(ACI_Midrange ~ Tot_Knocks + Num_Herbivory + Num_L_calls + Year + Hour + lunar.phase.sine, data = AC.DF1Co)
mf.aci1year <-  lm(ACI_Midrange ~ Tot_Knocks + Num_Herbivory + Num_L_calls + Year + Hour, data = AC.DF1Co)

```


```{r mf acimax sine vs year, echo = FALSE}

#maximal model
mf.maxaci.sine <- lm(ACI_Midrange ~ (Tot_Knocks + Num_L_calls + Num_Herbivory)*Hour + lunar.phase.sine, data = AC.DF1Co)
mf.maxaci.combo <- lm(ACI_Midrange ~ (Tot_Knocks + Num_L_calls + Num_Herbivory)*Hour + Year + lunar.phase.sine, data = AC.DF1Co)
mf.maxaci.year <- lm(ACI_Midrange ~ (Tot_Knocks + Num_L_calls + Num_Herbivory)*Hour + Year, data = AC.DF1Co)

```


```{r mf aci2 sine vs year , echo = FALSE}

mf.aci2sine <- lm(ACI_Midrange ~ Tot_Knocks + Hour + lunar.phase.sine, data = AC.DF1Co)
mf.aci2combo <- lm(ACI_Midrange ~ Tot_Knocks + Hour + Year + lunar.phase.sine, data = AC.DF1Co)
mf.aci2year <- lm(ACI_Midrange ~ Tot_Knocks + Hour + Year, data = AC.DF1Co)

```


```{r mfaci3 sine vs year, echo = FALSE}

mf.aci3sine <- lm(ACI_Midrange ~ Tot_Knocks*Hour + lunar.phase.sine, data = AC.DF1Co)
mf.aci3combo <- lm(ACI_Midrange ~ Tot_Knocks*Hour + Year + lunar.phase.sine, data = AC.DF1Co)
mf.aci3year <- lm(ACI_Midrange ~ Tot_Knocks*Hour + Year, data = AC.DF1Co)


```

###Model Selection

```{r mf aci sine vs year model selection, echo = TRUE}

acimftbl <-AICc(mf.aci1sine, mf.aci1combo, mf.aci1year, mf.aci2sine, mf.aci2combo, mf.aci2year, mf.aci3sine, mf.aci3combo, mf.aci3year, mf.maxaci.sine, mf.maxaci.combo, mf.maxaci.year)

acimftbl$minAIC <- 4058.838
acimftbl$deltaAIC <- acimftbl$AICc - acimftbl$minAIC

acimftbl

acimftbl.short <- subset(acimftbl, deltaAIC < 6)

acimftbl.short

```


```{r summary sine aci year mf, echo = TRUE}
summary(mf.aci2sine)
summary(mf.aci2year)
```

Now knocks are significant... I wonder if this comes from centering using arm rather than center_scale.

However, this model still explains 2% of variation and is not significant.

Neither Year or sine are significant here.
