---
title: "Results_NEW_ALL"
author: "Sean Dimoff"
date: 27/05/20
output: 
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
---

```{r setup, include=FALSE}
library(ggplot2)
library(cowplot)
library(rmarkdown)
library(knitr)
library(RColorBrewer)
library(GGally)
library(mctest)
library(usdm)
library(hms)
library(dplyr)
library(lme4)
library(MASS)
library(lmerTest)
library(goft)
library(magick)
library(MuMIn)
library(car)
library(gridExtra)
library(patchwork)
library(arm)
#library(sjPlot)
#library(sjlabelled)
#library(sjmisc)


#loading in SPL data

load("../Raw_Data/SPLHF17long.Rdata")
load("../Raw_Data/SPLHF18long.Rdata")


load("../Raw_Data/SPLMF17long.Rdata")
load("../Raw_Data/SPLMF18long.Rdata")


load("../Raw_Data/SPLHFlong.Rdata")
load("../Raw_Data/SPLMFlong.Rdata")

load("../Raw_Data/SPLMF.long.wind.Rdata")

#combined SPL and HF dataframes
load("../Raw_Data/Snap.HF17.Rdata")
load("../Raw_Data/Snap.HF18.Rdata")
#changing site to a character
Snap.HF17$Site.x <- as.character(Snap.HF17$Site.x)
Snap.HF18$Site.x <- as.character(Snap.HF18$Site.x)

load("../Raw_Data/Snap.HF.Rdata")

##loading in the full dataframe with all data
#load("../Raw_Data/AC.DF.Rdata")
load("../Raw_Data/AC.DF1.Rdata")

#loading in boat.list
load("../Raw_Data/boatlist.Rdata")

#loading in MF ACI data for diurnal plot
load("../Raw_Data/ACI_MF_tot.Rdata")

#loading in Selection tables
sel.tbl <- read.csv("../Raw_Data/Knock_Selections.csv")

#removing site/date id's from AC.DF1 that have boat noise in the files
AC.DF1 <- AC.DF1[!(AC.DF1$st.id %in% boat.list),]

#removes 4 from 40, 2 from 32, 1 from 35, and one from 5

#making site a character
AC.DF1$Site <- as.character(AC.DF1$Site)

#making duplicate dataframes
AC.DF1C <- AC.DF1

Snap.HF17C <- Snap.HF17
Snap.HF18C <- Snap.HF18

#Creating centered AC.DF1 dataframe
AC.DF1C$Snaps <- rescale(AC.DF1C$Snaps, "center")
AC.DF1C$Tot_Knocks <- rescale(AC.DF1C$Tot_Knocks, "center")
AC.DF1C$Num_Herbivory <- rescale(AC.DF1C$Num_Herbivory, "center")
AC.DF1C$Num_L_calls <- rescale(AC.DF1C$Num_L_calls, "center")

#creating centered Snap.HF17 and 18 dataframes
Snap.HF17C$SPL_HF <- rescale(Snap.HF17C$SPL_HF, "center")
Snap.HF18C$SPL_HF <- rescale(Snap.HF18C$SPL_HF, "center")


#removing outliers from Snap.HF dataframe
low.snap <- Snap.HF[Snap.HF$Snaps <1000, ]
# Remove anything with fewer than 2 observers 
Snap.HF <- Snap.HF[!(Snap.HF$ds.id %in% low.snap$ds.id),]

#Centering snaps
Snap.HF$Snaps <- rescale(Snap.HF$Snaps, "center")

#subsetting only lm variables
AC.DF1Co <- subset(AC.DF1C, select = c(SPL_Midrange, ACI_Midrange, Tot_Knocks, Num_L_calls, Num_Herbivory, Site, Hour, Year, Date))

#making Hour ordinal
#AC.DF1Co$Hour_factor <- factor (AC.DF1$Hour, order = TRUE, levels = c("3", "9", "15", "21"))


#splitting dataframe by site
s5 <- filter(AC.DF1, Site == "5")
s32 <- filter(AC.DF1, Site == "32")
s35 <- filter(AC.DF1, Site == "35")
s40 <- filter(AC.DF1, Site == "40")
s8 <- filter(AC.DF1, Site == "8")

#splitting dataframe by hour
h3 <- filter(AC.DF1, Hour == "3")
h9 <- filter(AC.DF1, Hour == "9")
h15 <- filter(AC.DF1, Hour == "15")
h21 <- filter(AC.DF1, Hour == "21")

#creating new variable for site_year
Snap.HF$site_year <- paste(Snap.HF$Site, Snap.HF$Year, sep= "_")
AC.DF1Co$site_year <- paste(AC.DF1Co$Site, AC.DF1Co$Year, sep= "_")


#Adding in continuous fishing pressure variable to dataframes used for modelling
sites <- read.csv("../Raw_Data/KI_Sites_Sept2019.csv", header = TRUE, stringsAsFactors = FALSE)
#renaming the first column so that it doesn't have unknown characters
colnames(sites)[1] <- "site"

Snap.HF$fp.cont <-  sites$continous.pressure.2km[match(Snap.HF$Site, sites$site)]
AC.DF1Co$fp.cont <- sites$continous.pressure.2km[match(AC.DF1Co$Site, sites$site)]

#centering fp.cont
Snap.HF$fp.cont <- rescale(Snap.HF$fp.cont, "center")
AC.DF1Co$fp.cont <- rescale(AC.DF1Co$fp.cont, "center")

##loading in lunar phase data
#load("../Raw_Data/LunarPhase2017.Rdata")
#load("../Raw_Data/LunarPhase2018.Rdata")
load("../Raw_Data/LunarPhase2017_format.Rdata")
load("../Raw_Data/LunarPhase2018_format.Rdata")
#save(lp2018a, file = "../Raw_Data/LunarPhase2018_format")

#combining these dataframes
#Lunar.phase.snap <- rbind(lp2017, lp2018)
Lunar.phase.fish <- rbind(lp2017a, lp2018a)
#matching lunar phase  #never this easy - the dates don't match up, need to investigate
Snap.HF$lunar.phase.sine <- Lunar.phase.fish$lunar.sine.x[match(Snap.HF$Date, Lunar.phase.fish$Date.b)]
Snap.HF$lunar.phase.cos <- Lunar.phase.fish$lunar.cos.x[match(Snap.HF$Date, Lunar.phase.fish$Date.b)]

AC.DF1Co$lunar.phase.sine <- Lunar.phase.fish$lunar.sine.x[match(AC.DF1Co$Date, Lunar.phase.fish$Date.a)]
AC.DF1Co$lunar.phase.cos <- Lunar.phase.fish$lunar.cos.x[match(AC.DF1Co$Date, Lunar.phase.fish$Date.a)]

sum(is.na(Snap.HF$lunar.phase.sine))
sum(is.na(Snap.HF$lunar.phase.cos))
sum(is.na(AC.DF1Co$lunar.phase.sine))
sum(is.na(AC.DF1Co$lunar.phase.cos))
#need to add date to the AC.DF1Co 

```

**Exploratory Plots for 2017-2018 Acoustic/Fish Data**

**Purpose** To run and select my new final models for the acoustic manuscript

I have summarized results at the top here, but please scroll down if you would like to see the outputs of the linear models and further analysis into each of the selected models.

*Note* 

Any models that use MF - are actually my low frequency models - this is just an artifact from the beginning of the project.

fishing pressure has now been centered.

In the low frequencies, Lunar phase category "First Quarter" cannot be analyzed because it is the only category of lunar phase in 2018 and therefore they are collinear.

#Results Summarized


**SPL HF**

The selected model was the "best" model according to AIC.  It included:

*Snaps x Day/Night + lunar phase + Year + fishing pressure*

All were significant.

It explains 37.14% of the variation in HF SPL.

**SPL LF**

The selected model was not the "best" model according to AIC.

The "best" model was maximal. But the selected model was within delta AIC < 2 and had several fewer df.

This selected model included:

*Knocks x Hour + Herbivory + Year + Lunar Phase + fishing pressure*

The interaction between knocks and 9AM was the only significant interaction and was strongly positive.

Herbivory was significant as well with a small positive effect.

Year was also significant.

Lunar phase and fishing pressure were not significant.

This model explains 53% of variation in LF SPL. 


**ACI HF **

The selected model was not the "best" model according to AIC.

All 3 models were within delta AIC <2.  So I chose the model with the fewest df.  It was the only model that didn't include day/night 
(which was not significant in any models).

The chosen model included:

*Snaps + Year + lunar phase + fishing pressure*

Only snaps and fishing pressure were significant. 

Snaps had a really small effect size, fishing pressure was larger.

The model is significant but probably due to the enormous sample size (n > 15,000)

This model only explained 7.5% of variation in ACI.


**ACI LF**

The selected model was the "best" model according to AIC.

One other similar model fell within delta AIC < 4, but it had 2 more df (it included herbivory and long calls).

Neither model is significant however.

The chosen model included:

*Knocks + Hour + Year + lunar phase + fishing pressure*

Within the chosen model only knocks were significant, with a reasonable effect size (~3000).

This model only explains 1.2% of variation in LF ACI.


#Final Model selection
## SPL HF Model


```{r simple model sin vs. year, echo = TRUE}
Snap.HF$Year <- as.character(Snap.HF$Year)

simple.model <- lm(SPL_HF ~ Snaps + Year + lunar.phase.sine + fp.cont, data = Snap.HF)
summary(simple.model)
```


```{r simple model2 sin vs. year, echo= TRUE}
simple.model1<- lm(SPL_HF ~ Snaps + dn + Year + lunar.phase.sine + fp.cont, data = Snap.HF)
```



```{r simple model3 sin vs. year, echo = TRUE}

simple.model3 <- lm(SPL_HF ~ Snaps*dn + lunar.phase.sine + Year + fp.cont, data = Snap.HF)
plot(simple.model3)
summary(simple.model3)
```

###Model Selection

```{r hf sin vs year spl selection, echo = TRUE}

#coming up with several variations on the models presented above

#testing each of the models

splhftbl <- AICc(simple.model, simple.model1, simple.model3)

splhftbl$minAIC <- 77923.39
splhftbl$deltaAIC <- splhftbl$AICc - splhftbl$minAIC

splhftbl
summary(simple.model)
summary(simple.model1)
summary(simple.model3)

```




## ACI HF Model

```{r hf sine vs year aci step, echo = TRUE}
aci.hf <- lm(ACI_HF ~ Snaps*dn + Year + lunar.phase.sine + fp.cont, data = Snap.HF)
aci.hf1 <- lm(ACI_HF ~ Snaps + Year + lunar.phase.sine + fp.cont, data = Snap.HF)
aci.hf2 <- lm(ACI_HF ~ Snaps+ dn + Year + lunar.phase.sine + fp.cont, data = Snap.HF)


acihftbl <- AICc(aci.hf, aci.hf1, aci.hf2)
acihftbl$minAIC <- 319647.7
acihftbl$deltaAIC <- acihftbl$AICc - acihftbl$minAIC
acihftbl

summary(aci.hf)
summary(aci.hf2)
summary(aci.hf1)

```

I am choosing the aci.hf1 model here which does not include day/night.  This is because it has the lowest df, but also is within delta AIC < 2.


## LF SPL Model


```{r sine vs year 1 mf model, echo = TRUE}


simple1mf <- lm(SPL_Midrange ~ Tot_Knocks + lunar.phase.sine + Year + fp.cont, data = AC.DF1Co)


```


```{r sine vs year 2 mf model, echo = TRUE}

simple2mf <- lm(SPL_Midrange ~ Tot_Knocks + Num_Herbivory + Num_L_calls + Hour + Year + lunar.phase.sine + fp.cont, data = AC.DF1Co)

```



```{r simple4 year mf model, echo = TRUE}


simple4mf<- lm(SPL_Midrange ~ Tot_Knocks + Num_Herbivory + Num_L_calls + Hour + Tot_Knocks:Hour + Year + lunar.phase.sine + fp.cont, data = AC.DF1Co)

#All call types affect MF SPL, however, only knocks changes its effect size throughout the day

```


```{r simple7 year mf model, echo = TRUE}



simplemaxmf <- lm(SPL_Midrange ~ Tot_Knocks + Num_Herbivory + Num_L_calls + Hour + Year + Tot_Knocks:Hour + Num_Herbivory:Hour + Num_L_calls:Hour + lunar.phase.sine + fp.cont, data = AC.DF1Co)

summary(simplemaxmf)
```

```{r simple year reduced mf models, echo = TRUE}


reducemf4 <- lm(SPL_Midrange ~ Tot_Knocks + Hour + Tot_Knocks:Hour + Year + lunar.phase.sine + fp.cont, data = AC.DF1Co)
#The effect of knocks on MF SPL changes throughout the day



reducemf6 <- lm(SPL_Midrange ~ Tot_Knocks + Hour + Tot_Knocks:Hour + Num_Herbivory + Year + lunar.phase.sine + fp.cont, data = AC.DF1Co)

reducemf7 <- lm(SPL_Midrange ~ Tot_Knocks + Hour + Tot_Knocks:Hour + Num_Herbivory + Year, data = AC.DF1Co)
#the effect of knocks on MF SPL changes throughout the day and herbivory is also loud enough to affect MF SPL


```



###Model Selection


```{r model year selection mf spl, echo = TRUE}

splmftbl <- AICc(simple1mf, simple2mf, simple4mf, simplemaxmf, reducemf4, reducemf6)

splmftbl$minAIC <- 884.2740
splmftbl$deltaAIC <- splmftbl$AICc - splmftbl$minAIC

splmftbl

splmftbl.short <- subset(splmftbl, deltaAIC < 6)

splmftbl.short

summary(simplemaxmf)
summary(reducemf6)
summary(reducemf7)
summary(simple4mf)


```

The new best model is the one that was our second best model originally and also includes herbivory


## LF ACI Model

```{r mf aci1 sine vs year, echo = TRUE}


mf.aci1 <- lm(ACI_Midrange ~ Tot_Knocks + Num_Herbivory + Num_L_calls + Year + Hour + lunar.phase.sine + fp.cont, data = AC.DF1Co)

```


```{r mf acimax sine vs year, echo = TRUE}

#maximal model

mf.maxaci <- lm(ACI_Midrange ~ (Tot_Knocks + Num_L_calls + Num_Herbivory)*Hour + Year + lunar.phase.sine + fp.cont, data = AC.DF1Co)


```


```{r mf aci2 sine vs year , echo = TRUE}


mf.aci2 <- lm(ACI_Midrange ~ Tot_Knocks + Hour + Year + lunar.phase.sine + fp.cont, data = AC.DF1Co)


```


```{r mfaci3 sine vs year, echo = TRUE}


mf.aci3 <- lm(ACI_Midrange ~ Tot_Knocks*Hour + Year + lunar.phase.sine + fp.cont, data = AC.DF1Co)

mf.aci4 <- lm(ACI_Midrange ~ Tot_Knocks*Hour + Num_Herbivory + Year + lunar.phase.sine + fp.cont, data = AC.DF1Co)

```

###Model Selection

```{r mf aci sine vs year model selection, echo = TRUE}

acimftbl <-AICc(mf.aci1, mf.maxaci, mf.aci2, mf.aci3, mf.aci4)

acimftbl$minAIC <- 4062.712
acimftbl$deltaAIC <- acimftbl$AICc - acimftbl$minAIC

acimftbl

acimftbl.short <- subset(acimftbl, deltaAIC < 6)

acimftbl.short

```


```{r summary sine aci year mf, echo = TRUE}
summary(mf.aci2)
summary(mf.aci3)
summary(mf.aci1)
```

Now knocks are significant... I wonder if this comes from centering using arm rather than center_scale.

However, this model still explains 1.2% of variation and is not significant.

