---
title: "Results_No_Random_Lunar_Rerun"
author: "Sean Dimoff"
date: 25/05/20
output: 
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
---

```{r setup, include=FALSE}
library(ggplot2)
library(cowplot)
library(rmarkdown)
library(knitr)
library(RColorBrewer)
library(GGally)
library(mctest)
library(usdm)
library(hms)
library(dplyr)
library(lme4)
library(MASS)
library(lmerTest)
library(goft)
library(magick)
library(MuMIn)
library(car)
library(gridExtra)
library(patchwork)
library(arm)
#library(sjPlot)
#library(sjlabelled)
#library(sjmisc)


#loading in SPL data

load("../Raw_Data/SPLHF17long.Rdata")
load("../Raw_Data/SPLHF18long.Rdata")


load("../Raw_Data/SPLMF17long.Rdata")
load("../Raw_Data/SPLMF18long.Rdata")


load("../Raw_Data/SPLHFlong.Rdata")
load("../Raw_Data/SPLMFlong.Rdata")

load("../Raw_Data/SPLMF.long.wind.Rdata")

#combined SPL and HF dataframes
load("../Raw_Data/Snap.HF17.Rdata")
load("../Raw_Data/Snap.HF18.Rdata")
#changing site to a character
Snap.HF17$Site.x <- as.character(Snap.HF17$Site.x)
Snap.HF18$Site.x <- as.character(Snap.HF18$Site.x)

load("../Raw_Data/Snap.HF.Rdata")

##loading in the full dataframe with all data
#load("../Raw_Data/AC.DF.Rdata")
load("../Raw_Data/AC.DF1.Rdata")

#loading in boat.list
load("../Raw_Data/boatlist.Rdata")

#loading in MF ACI data for diurnal plot
load("../Raw_Data/ACI_MF_tot.Rdata")

#loading in Selection tables
sel.tbl <- read.csv("../Raw_Data/Knock_Selections.csv")

#removing site/date id's from AC.DF1 that have boat noise in the files
AC.DF1 <- AC.DF1[!(AC.DF1$st.id %in% boat.list),]

#removes 4 from 40, 2 from 32, 1 from 35, and one from 5

#making site a character
AC.DF1$Site <- as.character(AC.DF1$Site)

#making duplicate dataframes
AC.DF1C <- AC.DF1

Snap.HF17C <- Snap.HF17
Snap.HF18C <- Snap.HF18

#Creating centered AC.DF1 dataframe
AC.DF1C$Snaps <- rescale(AC.DF1C$Snaps, "center")
AC.DF1C$Tot_Knocks <- rescale(AC.DF1C$Tot_Knocks, "center")
AC.DF1C$Num_Herbivory <- rescale(AC.DF1C$Num_Herbivory, "center")
AC.DF1C$Num_L_calls <- rescale(AC.DF1C$Num_L_calls, "center")

#creating centered Snap.HF17 and 18 dataframes
Snap.HF17C$SPL_HF <- rescale(Snap.HF17C$SPL_HF, "center")
Snap.HF18C$SPL_HF <- rescale(Snap.HF18C$SPL_HF, "center")


#removing outliers from Snap.HF dataframe
low.snap <- Snap.HF[Snap.HF$Snaps <1000, ]
# Remove anything with fewer than 2 observers 
Snap.HF <- Snap.HF[!(Snap.HF$ds.id %in% low.snap$ds.id),]

#making a snap.hf dataframe to center
Snap.HFC <- Snap.HF

Snap.HFC$Snaps <- rescale(Snap.HFC$Snaps, "center")

#subsetting only lm variables
AC.DF1Co <- subset(AC.DF1C, select = c(SPL_Midrange, ACI_Midrange, Tot_Knocks, Num_L_calls, Num_Herbivory, Site, Hour, Year, Date))

#making Hour ordinal
#AC.DF1Co$Hour_factor <- factor (AC.DF1$Hour, order = TRUE, levels = c("3", "9", "15", "21"))


#splitting dataframe by site
s5 <- filter(AC.DF1, Site == "5")
s32 <- filter(AC.DF1, Site == "32")
s35 <- filter(AC.DF1, Site == "35")
s40 <- filter(AC.DF1, Site == "40")
s8 <- filter(AC.DF1, Site == "8")

#splitting dataframe by hour
h3 <- filter(AC.DF1, Hour == "3")
h9 <- filter(AC.DF1, Hour == "9")
h15 <- filter(AC.DF1, Hour == "15")
h21 <- filter(AC.DF1, Hour == "21")

#creating new variable for site_year
Snap.HF$site_year <- paste(Snap.HF$Site, Snap.HF$Year, sep= "_")
AC.DF1Co$site_year <- paste(AC.DF1Co$Site, AC.DF1Co$Year, sep= "_")


#Adding in continuous fishing pressure variable to dataframes used for modelling
sites <- read.csv("../Raw_Data/KI_Sites_Sept2019.csv", header = TRUE, stringsAsFactors = FALSE)
#renaming the first column so that it doesn't have unknown characters
colnames(sites)[1] <- "site"

Snap.HF$fp.cont <-  sites$continous.pressure.2km[match(Snap.HF$Site, sites$site)]
AC.DF1Co$fp.cont <- sites$continous.pressure.2km[match(AC.DF1Co$Site, sites$site)]

#centering fp.cont
Snap.HF$fp.cont <- rescale(Snap.HF$fp.cont, "center")
AC.DF1Co$fp.cont <- rescale(AC.DF1Co$fp.cont, "center")

##loading in lunar phase data
#load("../Raw_Data/LunarPhase2017.Rdata")
#load("../Raw_Data/LunarPhase2018.Rdata")
load("../Raw_Data/LunarPhase2017_format.Rdata")
load("../Raw_Data/LunarPhase2018_format.Rdata")
#save(lp2018a, file = "../Raw_Data/LunarPhase2018_format")

#combining these dataframes
#Lunar.phase.snap <- rbind(lp2017, lp2018)
Lunar.phase.fish <- rbind(lp2017a, lp2018a)
#matching lunar phase  #never this easy - the dates don't match up, need to investigate
Snap.HF$lunar.phase.sine <- Lunar.phase.fish$lunar.sine.x[match(Snap.HF$Date, Lunar.phase.fish$Date.b)]
Snap.HF$lunar.phase.cos <- Lunar.phase.fish$lunar.cos.x[match(Snap.HF$Date, Lunar.phase.fish$Date.b)]

AC.DF1Co$lunar.phase.sine <- Lunar.phase.fish$lunar.sine.x[match(AC.DF1Co$Date, Lunar.phase.fish$Date.a)]
AC.DF1Co$lunar.phase.cos <- Lunar.phase.fish$lunar.cos.x[match(AC.DF1Co$Date, Lunar.phase.fish$Date.a)]

sum(is.na(Snap.HF$lunar.phase.sine))
sum(is.na(Snap.HF$lunar.phase.cos))
sum(is.na(AC.DF1Co$lunar.phase.sine))
sum(is.na(AC.DF1Co$lunar.phase.cos))
#need to add date to the AC.DF1Co 

```

**Exploratory Plots for 2017-2018 Acoustic/Fish Data**

**Purpose** To rerun my models with local disturbance as a continuous variable, year as a categorical variable, and lunar phase as a categorical variable.

I have summarized results at the top here, but please scroll down if you would like to see the outputs of the linear models and further analysis into each of the selected models, how they compare with my results when I included random effects, and comparisons between "matching" models if the new selected models aren't the same as those selected when random effects were included.

*Note* 

Any models that use MF - are actually my low frequency models - this is just an artifact from the beginning of the project.

fishing pressure has now been centered.

In the low frequencies, Lunar phase category "First Quarter" cannot be analyzed because it is the only category of lunar phase in 2018 and therefore they are collinear.

#Results Summarized



#Sine vs Cos Models
## SPL HF Model


```{r simple model sin vs. cos, echo = FALSE}
Snap.HF$Year <- as.character(Snap.HF$Year)
simple.model.sin <- lm(SPL_HF ~ Snaps + Year + lunar.phase.sine, data = Snap.HF)
simple.model.cos <- lm(SPL_HF ~ Snaps + Year + lunar.phase.cos, data = Snap.HF)

summary(simple.model.sin)
summary(simple.model.cos)
```

```{r simple model2 sin vs. cos, echo= FALSE}
simple.model1.sin <- lm(SPL_HF ~ Snaps + dn + Year + lunar.phase.sine, data = Snap.HF)
simple.model1.cos <- lm(SPL_HF ~ Snaps + dn + Year + lunar.phase.cos, data = Snap.HF)

summary(simple.model1.sin)
summary(simple.model1.cos)
```

```{r simple model3 sin vs. cos, echo = FALSE}

simple.model3.sin <- lm(SPL_HF ~ Snaps*dn + Year + lunar.phase.sine, data = Snap.HF)
simple.model3.cos <- lm(SPL_HF ~ Snaps*dn + Year + lunar.phase.cos, data = Snap.HF)

summary(simple.model3.sin)
summary(simple.model3.cos)
```

###Model Selection

```{r hf sin vs cos spl selection, echo = TRUE}

#coming up with several variations on the models presented above

#testing each of the models

splhftbl <- AICc(simple.model.sin, simple.model.cos, simple.model1.sin, simple.model1.cos, simple.model3.sin, simple.model3.cos)

splhftbl$minAIC <- 78411.93
splhftbl$deltaAIC <- splhftbl$AICc - splhftbl$minAIC

splhftbl
summary(simple.model3.sin)

```

**Same model is picked as when random effects are included**

Simple model 4 is the most parsimonious model. This is also my most saturated model.

Both Year and fp.cont are significant (3.4 dB louder in 2018) and fp.cont has a very small effect size (2.9 x10^-4).

All phases of the moon are significant - the full moon is the baseline.

This model explains about 37% of the variation in high frequency SPL - same as when lunar phase wasn't included.


## ACI HF Model

```{r hf aci step, echo = FALSE}
aci.hf <- lm(ACI_HF ~ Snaps + fp.cont + Year + lunar.phase, data = Snap.HF)



```

```{r hf aci day/night, echo = FALSE}
aci.hf1a <- lm(ACI_HF ~ dn + fp.cont + Year + lunar.phase, data = Snap.HF)



```


```{r hf aci step2, echo = FALSE}
aci.hf2 <- lm(ACI_HF ~ Snaps + dn + fp.cont + Year + lunar.phase, data = Snap.HF)



```


```{r hf aci step4, echo = FALSE}
aci.hf4 <- lm(ACI_HF ~ Snaps*dn + fp.cont + Year + lunar.phase, data = Snap.HF)


```


###Model Selection

```{r model selection aci hf, echo = TRUE}

acihftbl <- AICc(aci.hf, aci.hf1a, aci.hf2, aci.hf4)

acihftbl$minAIC <- 319640.0
acihftbl$deltaAIC <- acihftbl$AICc - acihftbl$minAIC

acihftbl


```

**This is not the same model as when we included random effects**

The most parsimonious model here is aci.hf.

```{r model summary acihf, echo = TRUE}
summary(aci.hf)

```

However, it only explains about 7.5% of the variation in ACI. A .5% increase from when lunar phase wasn't included.

Only the difference between the new moon and the full moon is present here. With an effect size of 329 (not huge considering ACI is in the 20,000's)

fp.cont is significant with a small effect size (-.7)

Year is now signiciant, although with a small effect size for ACI (-332)

When random effects were included we chose the model that included an interaction between snaps and day/night. The summary for the "matching" model without random effects is below

```{r model summary acihf4, echo = TRUE}
summary(aci.hf4)

```

fishing pressure is significant but Year is not.

Snaps is also significant but there is no significant change in their effect on ACI between day and night.

This model explains only about 7.5% of variation in HF ACI as well.

## LF SPL Model


```{r simple1a mf model, echo = FALSE}

simple1amf <- lm(SPL_Midrange ~ Tot_Knocks + fp.cont + Year + lunar.phase, data = AC.DF1Co)



```



```{r simple1b mf model, echo = FALSE}

simple1bmf <- lm(SPL_Midrange ~ Num_L_calls + fp.cont + Year + lunar.phase , data = AC.DF1Co)



```


```{r simple1c mf model, echo = FALSE}

simple1cmf <- lm(SPL_Midrange ~ Num_Herbivory + fp.cont + Year + lunar.phase, data = AC.DF1Co)


```


```{r simple2a mf model, echo = FALSE}

simple2amf <- lm(SPL_Midrange ~ Tot_Knocks + Num_Herbivory + fp.cont + Year + lunar.phase, data = AC.DF1Co)



```


```{r simple2b mf model, echo = FALSE}

simple2bmf <- lm(SPL_Midrange ~ Tot_Knocks + Num_L_calls + fp.cont + Year + lunar.phase, data = AC.DF1Co)



```


```{r simple2c mf model, echo = FALSE}

simple2cmf <- lm(SPL_Midrange ~ Tot_Knocks + Num_Herbivory + Num_L_calls + fp.cont + Year + lunar.phase, data = AC.DF1Co)



```


```{r simple3 mf model, echo = FALSE}

simple3mf <- lm(SPL_Midrange ~ Tot_Knocks + Num_Herbivory + Num_L_calls + Hour + fp.cont + Year + lunar.phase, data = AC.DF1Co)


```



```{r simple4 mf model, echo = FALSE}

simple4mf <- lm(SPL_Midrange ~ Tot_Knocks + Num_Herbivory + Num_L_calls + Hour + Tot_Knocks:Hour + fp.cont + Year + lunar.phase, data = AC.DF1Co)
#All call types affect MF SPL, however, only knocks changes its effect size throughout the day



```



```{r simple6a mf model, echo = FALSE}

simple6amf <- lm(SPL_Midrange ~ Tot_Knocks + Num_Herbivory + Num_L_calls + Hour + fp.cont + Year + Tot_Knocks:Hour + Num_Herbivory:Hour + lunar.phase, data = AC.DF1Co)


```


```{r simple6b mf model, echo = FALSE}

simple6bmf <- lm(SPL_Midrange ~ Tot_Knocks + Num_Herbivory + Num_L_calls + Hour + fp.cont + Year +
                  Tot_Knocks:Hour + Num_L_calls:Hour + lunar.phase, data = AC.DF1Co)

#All call types affect MF SPL, however, knocks and long calls change their effect sizes throughout the day


```


```{r simple7 mf model, echo = FALSE}

simple7mf <- lm(SPL_Midrange ~ Tot_Knocks + Num_Herbivory + Num_L_calls + Hour + fp.cont + Year + Tot_Knocks:Hour + Num_Herbivory:Hour + Num_L_calls:Hour + lunar.phase, data = AC.DF1Co)


```

```{r simple reduced mf models, echo = FALSE}




reducemf3 <- lm(SPL_Midrange ~ Tot_Knocks + Hour + fp.cont + Year + lunar.phase, data = AC.DF1Co)
#only knocks and year affect MF SPL

reducemf4 <- lm(SPL_Midrange ~ Tot_Knocks + Hour + Tot_Knocks:Hour + fp.cont + Year + lunar.phase, data = AC.DF1Co)
#The effect of knocks on MF SPL changes throughout the day

#reducemf5 <- lmer(SPL_Midrange ~ Tot_Knocks + Hour + Tot_Knocks:Hour + Num_L_calls + (1|Site)+(1|Year), data = AC.DF1Co)
#model fails to converge

reducemf6 <- lm(SPL_Midrange ~ Tot_Knocks + Hour + Tot_Knocks:Hour + Num_Herbivory + fp.cont + Year + lunar.phase, data = AC.DF1Co)
#the effect of knocks on MF SPL changes throughout the day and herbivory is also loud enough to affect MF SPL

reducemf7 <- lm(SPL_Midrange ~Tot_Knocks*lunar.phase + Hour + Tot_Knocks + Num_Herbivory + fp.cont + Year, data = AC.DF1Co)


```



###Model Selection


```{r model selection mf spl, echo = TRUE}

splmftbl <- AICc(simple1amf, simple1bmf, simple1cmf, simple2amf, simple2bmf, simple2cmf, simple3mf, simple4mf, simple6amf, simple6bmf, simple7mf, reducemf3, reducemf4, reducemf6, reducemf7)

splmftbl$minAIC <- 883.3541
splmftbl$deltaAIC <- splmftbl$AICc - splmftbl$minAIC

splmftbl

splmftbl.short <- subset(splmftbl, deltaAIC < 6)

splmftbl.short



```

I think here reducemf6 is the most respresentative model - it is the most parsimonious model in the end, but also explains roughly the same amount of variation in the response variable.

reducemf6: MF SPL ~ (Knocks * Hour) + Herbivory + Hour + Year + fp.cont + lunar.phase

```{r summary reducemf6, echo = TRUE}

summary(reducemf6)

```

Explains 53.7% of variation in MF SPL. Without lunar phase explained 53.6%.

Lunar.phasefirst quarter is coming up NA here, which means that "...it is linearly related to another variable..." which is year because first quarter is what every sampling day in 2018 was categorized as.

**This is not the same model selected as when we included random effects**

That model did not include herbivory.

fishing pressure is not significant.
Year is significant and 2018 is 3.7 dB louder than 2017.

The interaction between knocks and 9AM is still significant and positive.




Our "Best" model according to AIC is simple7mf:
simple7mf is a maximal model with all three types of fish sound interacting with hour:

simple7mf: MF SPL ~ (Knocks + Herbivory + Long Calls) * Hour + Year + fp.cont + lunar.phase

```{r summary simple7mf, echo = TRUE}

summary(simple7mf)

```


Adds 7 df, but only increases AIC by .5
Explains 56% of variation in MF SPL.

Lunar phase still not significant.


Our matching model - the one that is the same as the chosen model in our results that included a random effect is below.

```{r summary matching splmf, echo = TRUE}

summary(reducemf4)

```

Lunar phase is not significant.

fishing pressure is not significant.

Year is significant - 2018 is ~3.5 dB louder than 2017.



## LF ACI Model

```{r mf aci1, echo = FALSE}

mf.aci1 <- lm(ACI_Midrange ~ Tot_Knocks + fp.cont + Year + lunar.phase, data = AC.DF1Co)


```


```{r mf aci2a, echo = FALSE}

mf.aci2a <- lm(ACI_Midrange ~ Tot_Knocks + Num_Herbivory + fp.cont + Year + lunar.phase, data = AC.DF1Co)


```


```{r mf aci2b or Lon, echo = FALSE}

mf.aci2b <- lm(ACI_Midrange ~ Tot_Knocks + Num_L_calls + fp.cont + Year +lunar.phase, data = AC.DF1Co)


```


```{r mf aci3, echo = FALSE}

mf.aci3 <- lm(ACI_Midrange ~ Tot_Knocks + Num_Herbivory + Num_L_calls + fp.cont + Year +lunar.phase, data = AC.DF1Co)

```


```{r mf aci4, echo = FALSE}

mf.aci4 <- lm(ACI_Midrange ~ Tot_Knocks + Hour + fp.cont + Year + lunar.phase, data = AC.DF1Co)

#maximal model
mf.maxaci <- lm(ACI_Midrange ~ (Tot_Knocks + Num_L_calls + Num_Herbivory)*Hour + fp.cont + Year + lunar.phase, data = AC.DF1Co)

#reduced models
mf.acil <- lm(ACI_Midrange ~ Num_L_calls + fp.cont + Year + lunar.phase, data = AC.DF1Co)

mf.acih <- lm(ACI_Midrange ~Num_Herbivory + fp.cont + Year + lunar.phase, data = AC.DF1Co)

mf.acilh <- lm(ACI_Midrange ~ Num_L_calls*Hour + fp.cont + Year + lunar.phase, data = AC.DF1Co)

mf.acihh <- lm(ACI_Midrange ~ Num_Herbivory*Hour + fp.cont + Year + lunar.phase, data = AC.DF1Co)



```


```{r mf aci6, echo = FALSE}

fit.mfaci6 <- lm(ACI_Midrange ~ Tot_Knocks + Num_Herbivory + Num_L_calls + Hour + fp.cont + Year + lunar.phase, data = AC.DF1Co)



```


```{r mf aci7, echo = FALSE}

fit.mfaci7 <- lm(ACI_Midrange ~ Tot_Knocks*Hour + Num_Herbivory + Num_L_calls + fp.cont + Year + lunar.phase, data = AC.DF1Co)

#intercept model

#inter.mfaci <- lmer(ACI_Midrange ~ 1 + (1|site_year), data = AC.DF1Co)

```

###Model Selection

```{r mf aci model selection, echo = TRUE}

acimftbl <-AICc(mf.aci1, mf.aci2a, mf.aci2b, mf.aci3, mf.aci4, fit.mfaci6, fit.mfaci7, mf.maxaci, mf.acil, mf.acih, mf.acilh, mf.acihh)

acimftbl$minAIC <- 4056.976
acimftbl$deltaAIC <- acimftbl$AICc - acimftbl$minAIC

acimftbl

acimftbl.short <- subset(acimftbl, deltaAIC < 6)

acimftbl.short

```

**The selected model is different from the selected model including random effects**

The model with the lowest AIC here is my simplest model including only knocks, fishing pressure, year, and lunar phase.  
```{r summary mf.aci1, echo = TRUE}
summary(mf.aci1)

```
This model only explains 3% of variation in low frequency ACI.  Up from 2% w/o lunar phase.

The model is still not significant.

Fishing pressure is not significant
Year is not significant
Lunar phase is not significant



My maximal model (which matches my chosen model with random effects included), includes all call types and their interaction with hour.

```{r summary mf.maxaci, echo = TRUE}
summary(mf.maxaci)

```

It explains effectively 0.3% of variation in low frequency ACI when adjusted for the number of variables.





#Plots

##SPL

###High Frequency

```{r lunar phase plots, echo = FALSE}
p1 <- ggplot(Snap.HF, aes(x = lunar.phase, y = Snaps)) + geom_boxplot() + theme_classic()
p1

p2 <- ggplot(Snap.HF, aes(x = lunar.phase, y = SPL_HF)) + geom_boxplot() + theme_classic()
p2

```

Snaps do not change in frequency with each of the lunar phases... although I am including daytime recordings here too.

HF SPL is higher during new moons and first quarter moons. - similar finding to those in Staaterman 2014.

###High Frequency (Only night recordings)

**Subsetting only night recordings here**

```{r lunar phase night plots, echo = FALSE}
#subsetting just night
Snap.HFnight <- Snap.HF[(Snap.HF$dn == "Night"),]

p1n <- ggplot(Snap.HFnight, aes(x = lunar.phase, y = Snaps)) + geom_boxplot() + theme_classic()
p1n

p2n <- ggplot(Snap.HFnight, aes(x = lunar.phase, y = SPL_HF)) + geom_boxplot() + theme_classic()
p2n
```


This only seems to have shifted the y axis up, not suprisingly as we know HF SPL is higher at night.

There is still no difference in snaps, even just subsetting the night time recordings

The difference isn't obviously changed in HF SPL.

###Low Frequency

**Note** All first quarter moon phases are from 2018 and 2018 only.  All other moon phases are from 2017.

**Lit Check** Staaterman 2014 - Quietest during full moon and loudest during new moon at reefs in Hawaii and Florida

```{r mf lunar phase plots, echo = FALSE}
p3 <- ggplot(AC.DF1Co, aes(x = lunar.phase, y = Tot_Knocks)) + geom_boxplot() + theme_classic()
p3

p4 <- ggplot(AC.DF1Co, aes(x = lunar.phase, y = Num_L_calls)) + geom_boxplot() + theme_classic()
p4

p5 <- ggplot(AC.DF1Co, aes(x = lunar.phase, y = Num_Herbivory)) + geom_boxplot() + theme_classic()
p5

p6 <- ggplot(AC.DF1Co, aes(x = lunar.phase, y = SPL_Midrange)) + geom_boxplot() + theme_classic()
p6
```

###Low Frequency (Only 03:00 and 21:00 recordings)

```{r mf lunar phase night plots, echo = FALSE}
#subsetting only night recordings
nightrec <- c(3, 21)
AC.DF1Co.night <- AC.DF1Co[(AC.DF1Co$Hour %in% nightrec),]

p3n <- ggplot(AC.DF1Co.night, aes(x = lunar.phase, y = Tot_Knocks)) + geom_boxplot() + theme_classic()
p3n

p4n <- ggplot(AC.DF1Co.night, aes(x = lunar.phase, y = Num_L_calls)) + geom_boxplot() + theme_classic()
p4n

p5n <- ggplot(AC.DF1Co.night, aes(x = lunar.phase, y = Num_Herbivory)) + geom_boxplot() + theme_classic()
p5n

p6n <- ggplot(AC.DF1Co.night, aes(x = lunar.phase, y = SPL_Midrange)) + geom_boxplot() + theme_classic()
p6n

```

Full moon appears to have more knocks when I subset for only night.  However, there is still alot of overlap.

In the MF, SPL appears to be a bit lower, due to some outliers being removed. The same pattern of high SPL occurs in the new and first quarter moons here, matching what we see in the high frequencies.



##ACI

**Lit Check** - Staaterman 2014 - LF ACI had 2 peaks per lunar day - during quarter moon and new moon - at one of their sites but not the other

###High Frequency

```{r lunar phase aci, echo = FALSE}
p7 <- ggplot(Snap.HF, aes(x = lunar.phase, y = ACI_HF)) + geom_boxplot() + theme_classic()
p7
```


**Night Recordings Only **

```{r lunar phase aci night, echo = FALSE}
p7n <- ggplot(Snap.HFnight, aes(x = lunar.phase, y = ACI_HF)) + geom_boxplot() + theme_classic()
p7n
```

###Low Frequency

```{r lunar phase lf aci, echo = FALSE}
p8 <- ggplot(AC.DF1Co, aes(x = lunar.phase, y = ACI_Midrange)) + geom_boxplot() + theme_classic()
p8
```

**Night Recordings Only**

```{r lunar phase lf aci night, echo = FALSE}
p8n <- ggplot(AC.DF1Co.night, aes(x = lunar.phase, y = ACI_Midrange)) + geom_boxplot() + theme_classic()
p8n
```

HF ACI doesn't seem to change at all dependent on the moon phase

LF ACI "peaks" in the third quarter? Which is not what the literature supports. -- when I subset just at night that peak disappears.