---
title: "KI Reef Fish Data - Statistical Analysis"
author: "Jennifer Magel"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_depth: 2
---

```{r setup, include = FALSE}
# Load the data (abundance summed to site level, observers remain separate)
load("../Data/KI_UVC_13_15_17_obs_sum.Rdata")
load("../Data/KI_UVC_13_15_17_BM_obs_sum_ALL.Rdata")
waves_prod <- read.csv("../Data/KI_wave_prod_data_SESYNC.csv", stringsAsFactors = FALSE)

# Load necessary packages
library(ggplot2)
library(glmmADMB)
library(knitr)
library(kableExtra)
library(dplyr)
library(lme4)
library(arm)

# Set seed for random processes
set.seed(9)

# Order fishing pressure levels
ki_fish$f.pressure <- factor(ki_fish$f.pressure, levels(factor(ki_fish$f.pressure))[c(5,2,3,1,4)])
ki_fish_BM$f.pressure <- factor(ki_fish_BM$f.pressure, levels(factor(ki_fish_BM$f.pressure))[c(5,2,3,1,4)])

## Subset the data
sites_13 <- unique(ki_fish$Site[ki_fish$Year == "2013"])
sites_15 <- unique(ki_fish$Site[ki_fish$Year == "2015"])
sites_17 <- unique(ki_fish$Site[ki_fish$Year == "2017"])

sites_BDA <- Reduce(intersect, list(sites_13, sites_15, sites_17))

ki_fish <- filter(ki_fish, Site %in% sites_BDA)
ki_fish <- ki_fish[!(ki_fish$Site == "1"), ]
ki_fish <- ki_fish[!(ki_fish$Site == "3"), ]
ki_fish <- ki_fish[!(ki_fish$Site == "6"), ]
ki_fish <- ki_fish[!(ki_fish$Site == "25"), ]

ki_fish_BM <- filter(ki_fish_BM, Site %in% sites_BDA)
ki_fish_BM <- ki_fish_BM[!(ki_fish_BM$Site == "1"), ]
ki_fish_BM <- ki_fish_BM[!(ki_fish_BM$Site == "3"), ]
ki_fish_BM <- ki_fish_BM[!(ki_fish_BM$Site == "6"), ]
ki_fish_BM <- ki_fish_BM[!(ki_fish_BM$Site == "25"), ]

## Add SESYNC productivity data
ki_fish$npp_mean <- waves_prod$npp_mean[match(ki_fish$Site, waves_prod$Site)]
ki_fish$npp_max <- waves_prod$npp_max[match(ki_fish$Site, waves_prod$Site)]

ki_fish_BM$npp_mean <- waves_prod$npp_mean[match(ki_fish_BM$Site, waves_prod$Site)]
ki_fish_BM$npp_max <- waves_prod$npp_max[match(ki_fish_BM$Site, waves_prod$Site)]

# Rescale productivity variable
ki_fish$npp_max_z <- rescale(ki_fish$npp_max)
ki_fish_BM$npp_max_z <- rescale(ki_fish_BM$npp_max)
```

Fitting generalized linear mixed-effects models to model reef fish abundance, biomass, and species richness. Year and fishing pressure are included as fixed effects (plus an **interaction**) as well as productivity (npp_max), while Site and **Observer nested within Year** are included as random effects. Site 3 has been removed from the analysis, as this is the only site in the 'Low' disturbance category. Sites 1, 6, and 25 have also been removed, to trim the analysis down to three human disturbance levels (and avoid having 7 'medium' sites).


# Zeroes

Calculating the number of non-zero observations for each trophic group. Proportion of zeroes for groups with at least one zero observation: Corallivores = 9.8%, Detritivores = 8.0%, Generalist carnivores/Piscivores = 0.9%.

```{r zeroes, echo = FALSE}
zeroes <- as.data.frame(colSums(ki_fish[, c(7, 9:17)] != 0))
zeroes
```


# Total Abundance

```{r AB_total, echo = FALSE}
model1 <- glmmadmb(AB_total ~ Year * f.pressure + npp_max_z + (1|Site) + (1|Year/Observer), data = ki_fish, family = "nbinom")
plot(fitted(model1), resid(model1))
summary(model1)
```

## Means

```{r AB_total_mean, echo = FALSE}
ab <- aggregate(AB_total ~ Year, ki_fish, mean)
ab.sd <- aggregate(AB_total ~ Year, ki_fish, function(x) sd(x))
ab.se <- aggregate(AB_total ~ Year, ki_fish, function(x) sd(x)/sqrt(length(x)))
ab$SD <- ab.sd$AB_total
ab$SE <- ab.se$AB_total
ab
```


# Trophic Group Abundance
## Corallivores

```{r AB_coral, echo = FALSE}
model2 <- glmmadmb(AB_coral ~ Year * f.pressure + npp_max_z + (1|Site) + (1|Year/Observer), data = ki_fish, family = "nbinom")
plot(fitted(model2), resid(model2))
summary(model2)
```


## Detritivores

```{r AB_det, echo = FALSE}
model3 <- glmmadmb(AB_det ~ Year * f.pressure + npp_max_z + (1|Site) + (1|Year/Observer), data = ki_fish, zeroInflation = TRUE, family = "nbinom")
plot(fitted(model3), resid(model3))
summary(model3)
```


## Generalist Carnivores

```{r AB_gen, echo = FALSE}
model4 <- glmmadmb(AB_gen ~ Year * f.pressure + npp_max_z + (1|Site) + (1|Year/Observer), data = ki_fish, family = "nbinom")
plot(fitted(model4), resid(model4))
summary(model4)
```


## Herbivores

```{r AB_herb, echo = FALSE}
model5 <- glmmadmb(AB_herb ~ Year * f.pressure + npp_max_z + (1|Site) + (1|Year/Observer), data = ki_fish, family = "nbinom")
plot(fitted(model5), resid(model5))
summary(model5)
```


## Invertivores

```{r AB_inv, echo = FALSE}
model6 <- glmmadmb(AB_inv ~ Year * f.pressure + npp_max_z + (1|Site) + (1|Year/Observer), data = ki_fish, family = "nbinom")
plot(fitted(model6), resid(model6))
summary(model6)
```


## Omnivores

```{r AB_omn, echo = FALSE}
model7 <- glmmadmb(AB_omn ~ Year * f.pressure + npp_max_z + (1|Site) + (1|Year/Observer), data = ki_fish, family = "nbinom")
plot(fitted(model7), resid(model7))
summary(model7)
```


## Piscivores

```{r AB_pisc, echo = FALSE}
model8 <- glmmadmb(AB_pisc ~ Year * f.pressure + npp_max_z + (1|Site) + (1|Year/Observer), data = ki_fish, family = "nbinom")
plot(fitted(model8), resid(model8))
summary(model8)
```


## Planktivores

```{r AB_plank, echo = FALSE}
model9 <- glmmadmb(AB_plank ~ Year * f.pressure + npp_max_z + (1|Site) + (1|Year/Observer), data = ki_fish, family = "nbinom")
plot(fitted(model9), resid(model9))
summary(model9)
```


# Biomass

```{r BM_total, echo = FALSE}
model10 <- glmer(BM_total ~ Year * f.pressure + npp_max_z + (1|Site) + (1|Year/Observer), data = ki_fish_BM, family = Gamma(link = "log"), 
                control = glmerControl(optimizer = "bobyqa"))

plot(fitted(model10), resid(model10))
summary(model10)
```

## Means

```{r BM_total_mean, echo = FALSE}
bm <- aggregate(BM_total ~ Year, ki_fish_BM, mean)
bm.sd <- aggregate(BM_total ~ Year, ki_fish_BM, function(x) sd(x))
bm.se <- aggregate(BM_total ~ Year, ki_fish_BM, function(x) sd(x)/sqrt(length(x)))
bm$SD <- bm.sd$BM_total
bm$SE <- bm.se$BM_total
bm
```

# Species Richness

```{r SR_total, echo = FALSE}
model11 <- glmer(SR_total ~ Year * f.pressure + npp_max_z + (1|Site) + (1|Year/Observer), data = ki_fish, family = poisson(link = "log"))
plot(fitted(model11), resid(model11))
summary(model11)
```

## Means

```{r SR_total_mean, echo = FALSE}
sr <- aggregate(SR_total ~ Year, ki_fish, mean)
sr.sd <- aggregate(SR_total ~ Year, ki_fish, function(x) sd(x))
sr.se <- aggregate(SR_total ~ Year, ki_fish, function(x) sd(x)/sqrt(length(x)))
sr$SD <- sr.sd$SR_total
sr$SE <- sr.se$SR_total
sr
```

